### 2024-02-10 inputs/data/output/compileoutput.tex
prepare repo environnment and upload data

\documentclass[12pt,english]{article}
\usepackage{lmodern}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{natbib}
\geometry{verbose,tmargin=2.4cm,bmargin=2.4cm,lmargin=2.4cm,rmargin=2.4cm}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{setspace}
\doublespacing
\usepackage[unicode=true]{hyperref}
\usepackage[bottom]{footmisc}
%for tables
\usepackage{booktabs}
\usepackage{caption}
\usepackage{rotating}
\usepackage{csquotes}
\usepackage{placeins}
\usepackage{subfig}

\begin{document}
\title{Replication output for Intergenerational Persistence in Child Mortality}
\maketitle

\pagebreak
\setcounter{page}{1}

\FloatBarrier
\section{Main tables and figures}

%%%%%%%
% Table 1
%%%%%%%
\begin{table}
\begin{center}
\caption{Descriptive Statistics, Women Aged 20-49}
\label{table:sumstats}
\input{sumstat.tex}
\end{center}
\footnotesize{Note: Sample includes women with at least one sibling ever born from 119 Demographic and Health Surveys in 44 countries. Sampling weights are rescaled to reflect each survey's contribution to the sample.} 
\end{table}

%%%%%%%
% Figure 1
%%%%%%%
\begin{figure}[t]
    \caption{Share with Any Child Death, by Any Sibling Death}
    \label{figure:shares}
    \begin{center}
    \includegraphics[scale=1]{summary_plot_shares.pdf}
    \end{center}

\footnotesize{Note: For each five-year age group, we plot the share of women with at least one child death separately for women with and without deceased siblings. The within-survey component is the weighted average of the difference in shares within in each survey. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{figure}

%%%%%%%
% Table 2
%%%%%%%
\begin{table}[t]
\begin{center}
\caption{Pooled Estimates of Mortality Persistence}
\label{table:main}
\subfloat[A. Indicator of sibling death]{
{\resizebox{\textwidth}{!}{\input{u5_anysibs_full_nostar}}}
}
\par
\subfloat[B. Count of sibling deaths]{
{\resizebox{\textwidth}{!}{\input{u5_numsibs_full_nostar}}}
}

\end{center}
\footnotesize{Note: The reported estimates are logit odds ratios and Poisson incidence rate ratios. Brackets contain standard errors clustered at the survey cluster level. AME refers to the average marginal effect of sibling death(s); in the woman-level models, it is computed at age 49. All models include survey indicators. Woman-level models also include indicators for the woman's age in single years. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

%%%%%%%
% Table 3
%%%%%%%

\begin{table}[t]
\begin{center}
\caption{Adding Covariates}
\label{table:mediators}

\subfloat[A. All]{
{\resizebox{0.5\textwidth}{!}{\input{covariates_full.tex}}}
}
\par
\subfloat[B. Non-migrants]{
{\resizebox{0.5\textwidth}{!}{\input{covariates_nonmigrants.tex}}}
}
\par
\subfloat[C. Height]{
{\resizebox{0.5\textwidth}{!}{\input{covariates_height.tex}}}
}

\end{center}
\footnotesize{Note: This table reports odds ratios from birth-level logit regressions of under-5 child death on the number of under-5 sibling deaths, the number of siblings ever born, and the indicated explanatory variables. We omit clusters lacking variation in child mortality. Migrant status is available in 77 surveys; height is available in 103. Socioeconomic variables include maternal education and a wealth index based on principal component analysis over a vector of durable goods ownership indicators. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

%%%%%%%
% Table 4
%%%%%%%
\begin{table}
\begin{center}
\caption{Panel Analyses of Mortality Persistence over the Mortality Transition}
\label{table:panel}
\resizebox{\textwidth}{!}{
\input{aggregates_nostar.tex}
}
\end{center}
\footnotesize{Note: Each observation is a country-period cell. The dependent variable is the cell-specific mortality persistence odds ratio (OR) or average marginal effect (AME) estimated from a birth-level logit regression of under-5 death on the mother's number of under-5 sibling death, the mother's number of siblings ever born, and survey indicators. All cell-level regressions include country and period fixed effects. Brackets contain standard errors clustered at the country level.}
\end{table}

\FloatBarrier
\section{Appendix}
\renewcommand\thetable{A.\arabic{table}}    
\setcounter{table}{0}

%%%%%%%
% Table A.1
%%%%%%%
\begin{table}
\begin{center}
\caption{Demographic and Health Surveys in the Sample}
\label{table:surveylist}
\input{surveylist_countryyears_sample}
\end{center}
\end{table}

%%%%%%%
% Table A.2
%%%%%%%
\textbf{This table is not automated. The user can copy the estimates from the analysis code.}
\begin{table}
\begin{center}
\caption{Partial Correlations of Sibling and Child Under-5 Mortality, Women Aged 45-49}
\label{table:correlations}
\begin{tabular}{l c c}
\toprule
                &\multicolumn{1}{c}{\shortstack{Any child death and\\any sibling death}}&\multicolumn{1}{c}{\shortstack{\# child deaths and\\ \# sibling deaths}}\\\cmidrule(lr){2-2}\cmidrule(lr){3-3}
                &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}\\
\midrule
Within-survey correlation &    XX &    XX \\
                &  &  \\
Number of observations  &       XX &   XX   \\
\bottomrule
\end{tabular}
\end{center}
\footnotesize{Note: Partial correlations are computed after conditioning on survey indicators. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

%%%%%%%
% Table A.3
%%%%%%%
\begin{table}
\begin{center}
\caption{Mothers' vs. Daughters' Reports of Any Under-5 Death}
\label{table:daughter_vs_mom_any}
\begin{tabular}{l*{4}{c}}
\toprule
\input{momdaughter_any.tex}
\bottomrule
\end{tabular}
\end{center}
\footnotesize{Note: Sample includes coresident 15-19 year olds and their 30-49 year old mothers when both responded to the survey. Mothers and daughters are interviewed separately and privately. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

%%%%%%%
% Table A.4
%%%%%%%
\begin{table}
\begin{center}
\caption{Mothers' vs. Daughters' Reports of Any Under-5 Death}
\label{table:daughter_vs_mom_count}

\begin{tabular}{l*{9}{c}}
\toprule
\input{momdaughter_count.tex}
\bottomrule
\end{tabular}
\end{center}
\footnotesize{Note: Sample includes coresident 15-19 year olds and their 30-49 year old mothers when both responded to the survey. Mothers and daughters are interviewed separately and privately. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

%%%%%%%
% Table A.5
%%%%%%%
\begin{table}
\begin{center}
\caption{Pooled Birth-Level Logit Estimations by Gender}
\label{table:main_bygender}
\input{u5_bygender.tex}
\end{center}
\footnotesize{Note: The reported estimates are logit odds ratios. Brackets contain standard errors clustered at the survey cluster level. AME refers to the average marginal effect of the indicated measure of sibling death(s). All models include survey indicators. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{table}

\renewcommand\thefigure{A.\arabic{figure}}    
\setcounter{figure}{0}

%%%%%%%
% Figure A.1
%%%%%%%
\begin{figure}
    \caption{Sibship Size and Sibling Mortality}
    \label{figure:sibsizemort}
    \begin{center}
    \includegraphics[scale=1]{sibsize_mort.pdf}
    \end{center}
\footnotesize{Note: This figure plots the relationship between sibship size and sibling mortality rates. The unit of observation is the survey-sibsize cell. We regress the sibling under-5 mortality rate on sibship size indicators and survey indicators. Mortality rates are scaled from 0 to 1. Cells are weighted by the number of women. Spikes are 95\% confidence intervals based on standard errors clustered at the country level. Sampling weights are rescaled to reflect each survey's contribution to the cell.}
\end{figure}

%%%%%%%
% Figure A.2
%%%%%%%
\begin{figure}
    \caption{Log Odds of Any Child Death, by Any Sibling Death}
    \label{figure:logodds}
    \begin{center}
    \includegraphics[scale=1.25]{summary_plot_logodds.pdf}
    \end{center}
\footnotesize{Note: For each five-year age group, we plot the log odds of any under-5 child death separately for women with and without deceased siblings. The within-survey component is calculated in log odds using the within-survey component and share of women with no sibling deaths in Figure \ref{figure:shares}. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{figure}

%%%%%%%
% Figure A.3
%%%%%%%
\begin{figure}
    \caption{Mother-Level Logit Results by Age}
    \label{figure:logitbyage}
    \begin{center}
    \includegraphics[scale=1.2]{logit_by_age.pdf}
    \end{center}
\footnotesize{Note: This figure demonstrates the robustness of the woman-level logit estimates to age specific estimations. Point estimates and 95\% confidence intervals based on women-level logit regressions of any under-5 child death on any under-5 sibling death. All regressions include survey indicators and single-year age indicators. Pooled estimations include women of all ages; age-specific estimations are separate for each five-year age group. Average marginal effects are computed for the final age in each age interval; confidence intervals are based on standard errors computed using the delta method. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{figure}

%%%%%%%
% Figure A.4
%%%%%%%
\begin{figure}
    \caption{Comparison with Other Under-5 Mortality Differentials}
    \label{figure:gradients}
    \begin{center}
    \includegraphics[scale=1.2]{gradients.pdf}
    \end{center}
\footnotesize{Note: The top panel presents point estimates and 95\% confidence intervals of odds ratios from four woman-level logit regressions of any under-5 child death  on the indicated categorical variables in the figure. All regressions include survey indicators and single-year age indicators. The bottom panel presents histograms of the categorical variables. Sampling weights are rescaled to reflect each survey's contribution to the sample.}
\end{figure}

%%%%%%%
% Figure A.5
%%%%%%%
\begin{sidewaysfigure}
    \caption{Robustness to Survey-by-Age Group Effects}
    \label{figure:surveyXagegroup}
    \begin{center}
    \includegraphics[scale=1.5]{surveyXagegroup.pdf}
    \end{center}
\footnotesize{Note: We add survey-by-age group indicators to each regression from Table \ref{table:main}. We report the new estimates alongside the original estimates from Table \ref{table:main}. Spikes represent 95\% confidence intervals}
\end{sidewaysfigure}

%%%%%%%
% Figure A.6
%%%%%%%
\begin{sidewaysfigure}
    \caption{Monte Carlo Simulations of Measurement Error}
   \label{figure:measurement}
  \begin{center}
\includegraphics[scale=1.5]{simulation.pdf}
 \end{center}
\footnotesize{Note: This figure reports the impact of simulated measurement error on our mortality persistence estimates. We simulate the omission of reported deceased siblings for different probabilities of omission. For each positive probability, we draw the number of omitted deceased siblings from a binomial distribution 50 times. We estimate each regression from Table \ref{table:main} in each simulated dataset. We plot the mean exponentiated coefficient (odds ratio or incidence rate ratio) across the 50 draws. At p = 0, we plot the result from Table \ref{table:main}, with no simulated measurement error.}
\end{sidewaysfigure}

%%%%%%%
% Figure A.7
%%%%%%%
\begin{figure}
    \caption{Mortality Persistence by Country}
    \label{figure:countrylevel}
    \begin{center}
    \includegraphics[scale=2]{dot_whiskers.pdf}
    \end{center}
\footnotesize{Note: This figure reports mortality persistence estimates for each country in our sample. The plotted estimates are odds ratios from birth-level logit regressions of under-5 death on the mother's number of under-5 sibling deaths. All regressions include the mother's number of siblings ever born and survey indicators. Spikes represent 95\% confidence intervals based on standard errors clustered at the survey cluster level. Sampling weights are rescaled to reflect each survey's contribution to each country sample.}
\end{figure}

%%%%%%%
% Figure A.8
%%%%%%%
\begin{figure}
    \caption{Absolute Versus Proportional Mortality Persistence for a Binary Risk Factor}
    \label{figure:meVSor}
    \begin{center}
    \includegraphics[scale=1]{me_VS_or.pdf}
    \end{center}
\footnotesize{Note: Each ray from the origin specifies the relationship between the marginal effect and the odds ratio for a binary risk factor (e.g., any sibling death) at a given level of baseline mortality risk. At higher baseline mortality risk, a given odds ratio translates to a larger marginal effect. The mortality decline trajectories demonstrate possible paths for the odds ratio and marginal effect as mortality falls.}
\end{figure}

%%%%%%%
% Figure A.9
%%%%%%%
\begin{sidewaysfigure}
    \caption{Under-5 Mortality Rate over Time, by Country}
    \label{figure:u5series}
    \begin{center}    
    \includegraphics[scale=1.6]{q5_series.pdf}
    \end{center}
Note: Rates are scaled from 0 to 1.
\end{sidewaysfigure}

%%%%%%%
% Figure A.10
%%%%%%%
\begin{figure}
    \caption{Semi-Parametric Panel Analyses}
    \label{figure:semiparm}
    \begin{center}
    \includegraphics[scale=1.5]{semiparametric_cells.pdf}
    \end{center}
\footnotesize{Note: The figure replicates Table \ref{table:panel}, columns (1) and (5), but with under-5 mortality separated into 6 bins. The point estimates are the coefficients for 5 bin indicators, leaving out the lowest as the reference category. Spikes are 95\% confidence intervals based on standard errors clustered at the country level. OR is the odds ratio. AME is the average marginal effect. Each panel represents a separate cell-level regression including country and period fixed effects. Panel A corresponds to Table \ref{table:panel}, column (1), while the Panel B corresponds to Table \ref{table:panel}, column (3).}
\end{figure}

%%%%%%%
% Figure A.11
%%%%%%%
\begin{figure}
    \caption{Leave-One-Out Panel Analyses}
    \label{figure:leaveout}
    \includegraphics[scale=1.45]{leave_one_out.pdf}

\footnotesize{Note: This figure replicates Table \ref{table:panel}, columns (1) and (5), leaving out one country at a time. The point estimates report the cell-level association of the under-5 mortality rate with the intergenerational persistence of under-5 mortality, net of country fixed effects and period fixed effects. Spikes are 95\% confidence intervals based on standard errors clustered at the country level. OR is the odds ratio. AME is the average marginal effect. The left-hand panel corresponds to Table \ref{table:panel}, column (1), while the right-hand panel corresponds to Table \ref{table:panel}, column (3).}
\end{figure}

\end{document}

### 2024-02-10 scripts/05-replication.R

@@ -1,0 +1,19 @@
+#### Preamble ####
+# Purpose: Replicate Figures and Tables
+# Author: Sami El Sabri, Liban Timir
+# Date: 10 February 2023
+# Contact: sami.elsabri@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(haven)
+library(countrycode)
+library(ggplot2)
+
+#### Read data ####
+penn_world_data <- haven::read_dta("inputs/data/data/aggregates/pwt91.dta")
+un_wpp_data <- read_csv("inputs/data/data/aggregates/WPP2019_Period_Indicators_Medium.csv")
+ucdp_data <- haven::read_dta("inputs/data/data/aggregates/ucdp_prio/ucdp-prio-acd-201.dta")
+# cannot access DHS survey data right now but will add later

### 2024-02-10 outputs/paper/paper.qmd
started working on paper.qmd

---
title: "Shaping Future Wealth: Analyzing Lifetime Resources Among Norway's Young Adults (25-40)"
subtitle: "My subtitle if needed"
author: 
  - Sami El Sabri
  - Liban Timir
thanks: "Code and data are available at: https://github.com/samielsabri/reproduce_paper"
date: 02-13-2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-02-10 outputs/paper/paper.tex
started working on paper.qmd

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}

  \newcolumntype{d}{S[
    input-open-uncertainty=,
    input-close-uncertainty=,
    parse-numbers = false,
    table-align-text-pre=false,
    table-align-text-post=false
  ]}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Shaping Future Wealth: Analyzing Lifetime Resources Among Norway's Young Adults (25-40)},
  pdfauthor={Sami El Sabri; Liban Timir},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Shaping Future Wealth: Analyzing Lifetime Resources Among
Norway's Young Adults (25-40)\thanks{Code and data are available at:
https://github.com/samielsabri/reproduce\_paper}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Sami El Sabri \and Liban Timir}
\date{February 13, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\section{Introduction}\label{introduction}

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows.
Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

Some of our data is of penguins (Figure~\ref{fig-bills}), from Horst,
Hill, and Gorman (2020).

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-bills-1.pdf}

}

\caption{\label{fig-bills}Bills of penguins}

\end{figure}%

Talk more about it.

And also planes (Figure~\ref{fig-planes}). (You can change the height
and width, but don't worry about doing that until you have finished
every other aspect of the paper - Quarto will try to make it look nice
and the defaults usually work well once you have enough text.)

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-planes-1.pdf}

}

\caption{\label{fig-planes}Relationship between wing length and width}

\end{figure}%

Talk way more about it.

\section{Model}\label{model}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\subsection{Model set-up}\label{model-set-up}

Define \(y_i\) as the number of seconds that the plane remained aloft.
Then \(\beta_i\) is the wing width and \(\gamma_i\) is the wing length,
both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R (R Core Team 2022) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\subsubsection{Model justification}\label{model-justification}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\section{Results}\label{results}

Our results are summarized in Table~\ref{tbl-modelresults}.

\begin{table}

\caption{\label{tbl-modelresults}Explanatory models of flight time based
on wing width and wing length}

\centering{

\centering
\begin{tabular}[t]{lc}
\toprule
  & First model\\
\midrule
(Intercept) & \num{1.12}\\
 & (\num{1.70})\\
length & \num{0.01}\\
 & (\num{0.01})\\
width & \num{-0.01}\\
 & (\num{0.02})\\
\midrule
Num.Obs. & \num{19}\\
R2 & \num{0.320}\\
R2 Adj. & \num{0.019}\\
Log.Lik. & \num{-18.128}\\
ELPD & \num{-21.6}\\
ELPD s.e. & \num{2.1}\\
LOOIC & \num{43.2}\\
LOOIC s.e. & \num{4.3}\\
WAIC & \num{42.7}\\
RMSE & \num{0.60}\\
\bottomrule
\end{tabular}

}

\end{table}%

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

In Figure~\ref{fig-ppcheckandposteriorvsprior-1} we implement a
posterior predictive check. This shows\ldots{}

In Figure~\ref{fig-ppcheckandposteriorvsprior-2} we compare the
posterior with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-1.pdf}

}

\subcaption{\label{fig-ppcheckandposteriorvsprior-1}Posterior prediction
check}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-2.pdf}

}

\subcaption{\label{fig-ppcheckandposteriorvsprior-2}Comparing the
posterior with the prior}

\end{minipage}%

\caption{\label{fig-ppcheckandposteriorvsprior}Examining how the model
fits, and is affected by, the data}

\end{figure}%

\subsection{Diagnostics}\label{diagnostics}

Figure~\ref{fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

Figure~\ref{fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-1.pdf}

}

\subcaption{\label{fig-stanareyouokay-1}Trace plot}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-2.pdf}

}

\subcaption{\label{fig-stanareyouokay-2}Rhat plot}

\end{minipage}%

\caption{\label{fig-stanareyouokay}Checking the convergence of the MCMC
algorithm}

\end{figure}%

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{Palmerpenguins: Palmer Archipelago (Antarctica) Penguin Data}.
\url{https://doi.org/10.5281/zenodo.3960218}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2022. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\end{CSLReferences}

\end{document}

### 2024-02-10 outputs/paper/paper.qmd
wrote introduction draft

@@
 ---
-title: "Shaping Future Wealth: Analyzing Lifetime Resources Among Norway's Young Adults (25-40)"
+title: "Echoes Through Generations: The Permanence of Child Mortality in Moroccan Lineages"
 subtitle: "My subtitle if needed"
@@
 
+install.packages("gitcreds")
+
 library(tidyverse)
 library(palmerpenguins)
+library("gitcreds")
+
+gitcreds_set()
 ```
@@
 # Introduction
+As nations strive to improve child health outcomes, understanding the intergenerational persistence of child mortality provides crucial insights into the effectiveness of public health interventions.
+This paper zeroes in on Morocco, a context within the broader scope of 44 developing countries analyzed by Lu and Vogl, to explore this phenomenon in detail.
+Our focus is on delineating the nuanced patterns of child mortality across generations within Moroccan families and assessing the broader socio-economic and public health implications.
+
+Lu and Vogl’s study uncovers a potent and persistent connection between the child mortality experiences of grandmothers and their daughters, drawing on data from 119 Demographic and Health Surveys.
+In Morocco, the analysis sought to fill the critical gap in understanding the specific magnitude and characteristics of this relationship.
+The estimands in the study are primarily odds ratios and incidence rate ratios, which provide a measure of the relationship between a mother's experience of sibling death in childhood and her own child's mortality risk.
+In addition to these, the researchers computed average marginal effects to capture the absolute persistence of child mortality risk.
+By employing robust statistical techniques and controlling for potential confounders, this paper aims to provide a clear picture of intergenerational child mortality trends within Moroccan society.
+
+The methodology involved detailed regression analyses to ascertain the influence of familial, socio-economic, and geographical factors on child mortality rates.
+By dissecting this data, the study found evidence of a significant risk in child mortality that transcends generations, which remained substantial even after accounting for various covariates.
+The implications of these findings are profound, as they not only shed light on the persistent nature of health disparities but also challenge the prevailing narrative of universal health improvement.
+Understanding the roots and resilience of these disparities is crucial for the development of effective health policies and interventions.
+
+The paper is structured to first present the context and motivation for focusing on Morocco, followed by a description of the data and methodology.
+Subsequent sections discuss the results, their significance, and implications for Moroccan public health policies.
+Finally, the paper concludes with recommendations for future research and policy considerations, underscoring the need for targeted strategies to disrupt the cycle of intergenerational child mortality.
 

### 2024-02-13 outputs/paper/paper.qmd
wrote data section draft

@@
 
-install.packages("gitcreds")
+install.packages("ggplot2")
 
-library(tidyverse)
-library(palmerpenguins)
-library("gitcreds")
+library(ggplot2)
 
@@
 In Morocco, the analysis sought to fill the critical gap in understanding the specific magnitude and characteristics of this relationship.
-The estimands in the study are primarily odds ratios and incidence rate ratios, which provide a measure of the relationship between a mother's experience of sibling death in childhood and her own child's mortality risk.
+The estimands in the paper are primarily odds ratios and incidence rate ratios, which provide a measure of the relationship between a mother's experience of sibling death in childhood and her own child's mortality risk.
 In addition to these, the researchers computed average marginal effects to capture the absolute persistence of child mortality risk.
@@
 
-# Data {#sec-data}
+# Data: Focusing on Morocco's Intergenerational Child Mortality {#sec-data}
+
+The dataset for Lu and Vogl's study provides a detailed snapshot of child mortality rates across generations within Morocco.
+It encompasses demographic surveys capturing both historical and contemporary data, spanning several decades to allow for the assessment of persistence in child mortality rates from grandmothers to mothers.
+
+The variables within this dataset were carefully selected to reflect key indicators of health outcomes, socioeconomic status, and geographic identifiers for regional analysis within Morocco.
+These variables include include the number and ages of children who died, causes of death, maternal health indicators, education levels, household income, and access to health services, which are vital for understanding the intergenerational dynamics of child mortality.
+
+Data cleaning was especially important in this case, considering the challenges inherent in longitudinal and generational health data.
+This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records, which are typical in historical datasets.
+
+Summary statistics revealed the mean and median child mortality rates, the variance in socio-economic indicators among the surveyed families, and other health-related metrics.
+This aggregated data provided a foundation for understanding the base conditions of Moroccan families and any preliminary patterns indicating the persistence of child mortality across generations.
+
+Visual representations, such as graphs and tables, illustrated the distribution of mortality rates, the relationship between socio-economic factors and child mortality, and the regional differences within Morocco.
+These visuals helped to convey the depth and nuances of the intergenerational persistence observed in the Moroccan data.
+
+The appendices include detailed statistical tables, additional graphs showing complex data relationships, and extensive notes on the data cleaning and processing methodology.
+
+This description of the dataset was written with the general ethical practices of demographic and health research in mind and provides a narrative for a subset of data focused on Morocco.
+
+The precise quantification of child mortality rates captured not only the incidence of deaths but also the timing and causes.
+This entailed using measurement techniques and standard demographic health indicators like the under-five mortality rate (U5MR) or neonatal mortality rate (NMR), which are internationally recognized measures.
+
+Socioeconomic status was gauged using a composite index combining variables such as income, education, and occupation.
+These measurements were tailored to the Moroccan context to accurately reflect local economic conditions and societal structures.
+
+Demographic characteristics were measured using standard metrics such as age, sex, household size, and variables that capture migration or urban-rural residency, given Morocco's diverse landscape from bustling cities to rural areas.
+
+Measurement in this dataset was meticulous to ensure comparability across generations.
+For example, the paper needed to account for changes over time in how mortality or socioeconomic status is recorded and reported within Morocco.
+The potential for measurement error or bias would necessitate rigorous validation techniques, such as cross-referencing with other data sources or conducting field verifications.
+
+The dataset also included constructed variables, which are derived from raw data through transformations or computations to better capture the concepts under study.
+For instance, a constructed variable might be a mortality risk score that combines the number of sibling deaths with the ages at which they occurred.
+
+In the context of Morocco, the discussion of measurement would also address the cultural and linguistic considerations in the data collection process.
+Questionnaires and surveys needed to be accurately translated and culturally adapted to ensure the measurement is valid and reliable across different Moroccan communities.
+
+Incorporating a thorough discussion of measurement in relation to the dataset is essential to validate the paper's findings and to ensure that conclusions drawn are based on accurate and reliable data.
+This discussion would ultimately contribute to the paper's credibility and the robustness of its policy recommendations for Morocco.
 

### 2024-02-13 outputs/paper/paper.qmd
rewrote draft intro and data section

--- 2024-02-10 outputs/paper/paper.qmd
@@
 ---
-title: "Shaping Future Wealth: Analyzing Lifetime Resources Among Norway's Young Adults (25-40)"
+title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
 subtitle: "My subtitle if needed"
@@
 
-library(tidyverse)
-library(palmerpenguins)
+install.packages("ggplot2")
+
+library(ggplot2)
+
+gitcreds_set()
 ```
@@
 # Introduction
+In the evolving landscape of organizational psychology, the exploration of individual agency beliefs (particularly free will) and their impact on job satisfaction presents a compelling field of study.
+"Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction" by Feldman et al.
+embarks on this journey, unveiling the nuanced relationship between one's belief in free will and their subsequent job satisfaction across diverse cultural contexts.
+A focused exploration of this relationship within the context of the American workforce provides a valuable estimand, given the United States' strong emphasis on individualism, autonomy, and the freedom to shape one's destiny which are principles deeply ingrained in the national ethos.
+
+The paper addresses a significant gap in existing literature by articulating how free will beliefs, beyond serving as philosophical contemplations, exert a tangible influence on individuals' professional lives.
+Through a robust approach that includes longitudinal studies and cross-cultural analyses, the research highlights a consistent positive correlation between strong beliefs in free will and higher levels of job satisfaction.
+This relationship, significantly influenced by perceived autonomy, underscores the pivotal role of individual agency beliefs in the context of the American workplace, where personal freedom and self-determination are highly valued.
+
+The importance of this paper lies not only in its findings but also in its implications, offering practical insights for enhancing organizational culture and employee satisfaction within the American context.
+By highlighting the importance of fostering environments that champion autonomy and respect individual agency beliefs, the paper prompts business leaders and policymakers to rethink strategies for workplace management and development.
+This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.
+
+Structurally, the paper unfolds starting from its comprehensive methodology (including the six-month study of American online workers) to its extensive cross-cultural survey, which contextualizes the American data within a global framework.
+It then articulates the specific implications of free will beliefs for job satisfaction among American employees, weaving these insights into broader discussions on the interplay between cultural values, individual beliefs, and workplace dynamics.
+The concluding sections propose future research directions and practical applications, emphasizing the critical role of understanding and leveraging individual agency beliefs in cultivating a more motivated and satisfied workforce.
 
@@
 # Data {#sec-data}
+
+The dataset for the study provides a detailed snapshot of free will beliefs, job satisfaction, and perceived job autonomy among American online workers.
+
+The variables within this dataset were carefully selected to reflect key indicators of job satisfaction, belief in free will, job autonomy, and additional agency constructs for regional analysis within America.
+
+Data cleaning was especially important in this case, considering the challenges inherent in longitudinal and generational health data.
+This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records.
+The dataset underwent meticulous cleaning, addressing missing values and ensuring consistency across responses.
+Special attention was given to the reliability of scales used for measuring the core variables, with adjustments made to account for the online work setting of the participants.
+
+Summary statistics revealed the mean and median job satisfaction rates, the correlation in job autonomy, and other job-related metrics.
+This aggregated data provided a foundation for understanding the base conditions of the workplace and any preliminary patterns indicating the persistence of individual agency.
+
+Visual representations, such as graphs and tables, illustrated the distribution of job satisfaction, free will beliefs, and the relationship between the two.
+These visuals helped to convey the depth and nuances of the autonomy persistence observed in the American data.
+
+The appendices include detailed statistical tables, additional graphs showing complex data relationships, and extensive notes on the data cleaning and processing methodology.
+
+This description of the dataset was written with the general ethical practices of demographic research in mind and provides a narrative for a subset of data focused on America.
+
+The precise quantification of child mortality rates captured not only the incidence of deaths but also the timing and causes.
+This entailed using measurement techniques and standard demographic health indicators like the under-five mortality rate (U5MR) or neonatal mortality rate (NMR), which are internationally recognized measures.
+
+Socioeconomic status was gauged using a composite index combining variables such as income, education, and occupation.
+These measurements were tailored to the Moroccan context to accurately reflect local economic conditions and societal structures.
+
+Demographic characteristics were measured using standard metrics such as age, sex, household size, and variables that capture migration or urban-rural residency, given Morocco's diverse landscape from bustling cities to rural areas.
+
+Measurement in this dataset was meticulous to ensure comparability across generations.
+For example, the paper needed to account for changes over time in how mortality or socioeconomic status is recorded and reported within Morocco.
+The potential for measurement error or bias would necessitate rigorous validation techniques, such as cross-referencing with other data sources or conducting field verifications.
+
+The dataset also included constructed variables, which are derived from raw data through transformations or computations to better capture the concepts under study.
+For instance, a constructed variable might be a mortality risk score that combines the number of sibling deaths with the ages at which they occurred.
+
+In the context of Morocco, the discussion of measurement would also address the cultural and linguistic considerations in the data collection process.
+Questionnaires and surveys needed to be accurately translated and culturally adapted to ensure the measurement is valid and reliable across different Moroccan communities.
+
+Incorporating a thorough discussion of measurement in relation to the dataset is essential to validate the paper's findings and to ensure that conclusions drawn are based on accurate and reliable data.
+This discussion would ultimately contribute to the paper's credibility and the robustness of its policy recommendations for Morocco.
 

### 2024-02-13 inputs/data/mini_meta/minimetacor.R
deleted old files and added new files

@@ -1,0 +1,69 @@
+# mini meta analyses correlations functions
+
+
+# Installing all the required packages for this analysis (if not already installed)
+list.of.packages <- c("car", "foreign", "metafor", "Hmisc", "pequod", "openxlsx", "readxl")
+
+new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
+if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
+
+lapply(list.of.packages, library, character.only = TRUE)
+
+
+PrintMetaResult  <- function (metadataframe) {
+  print(summary(metadataframe))
+
+}
+
+PrintPlotMetaR  <- function (metadataframe) {
+  forest(metadataframe, xlab="Correlation", alim=c(-1,1))
+}
+
+PrintFunnelMetaR  <- function (metadataframe) {
+
+  
+  funnel(metadataframe,
+         level=0.95, 
+         xlim=c(-1,1))
+  legend(-.6, 0.0,
+         c("0.1 > p > 0.05", "0.05 > p > 0.01", "< 0.01"),
+         fill=c("darkgrey", "grey", "lightgrey"))
+  
+}
+
+CorMeta <- function (Correlation, SampleSize, StudyName) {
+
+  set.seed(513131)
+  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
+  mod <- rma(Correlation, vi, method = "REML", data = dat)
+  
+  return (mod)
+}
+
+CorMetaES <- function (Correlation, SampleSize, StudyName) {
+
+  set.seed(513131)
+  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
+  mod <- rma(Correlation, vi, method = "REML", data = dat)
+  
+  return (mod$b[1])
+}
+
+CorMetaESlow <- function (Correlation, SampleSize, StudyName) {
+  
+  set.seed(513131)
+  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
+  mod <- rma(Correlation, vi, method = "REML", data = dat)
+  
+  return (mod$ci.lb)
+}
+
+CorMetaEShigh <- function (Correlation, SampleSize, StudyName) {
+  
+  set.seed(513131)
+  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
[…]

### 2024-02-13 inputs/data/mini_meta/running-meta-r-correlational-syntax.R

@@ -1,0 +1,30 @@
+# this.dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
+# setwd(this.dir)
+source("minimetacor.R")
+
+idataset1 <- read.table("summary-time1.csv", header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
+str(idataset1)
+idataset1$Study
+
+odataset1<-CorMeta(idataset1$R, idataset1$N,idataset1$Study)
+str(odataset1)
+PrintMetaResult(odataset1)
+PrintPlotMetaR(odataset1)
+PrintFunnelMetaR(odataset1)
+predict(odataset1)
+confint(odataset1)
+baujat(odataset1)
+
+idataset2 <- read.table("summary-time2.csv", header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
+str(idataset2)
+idataset2$Study
+
+odataset2<-CorMeta(idataset2$R, idataset2$N,idataset2$Study)
+str(odataset2)
+PrintMetaResult(odataset2)
+PrintPlotMetaR(odataset2)
+PrintFunnelMetaR(odataset2)
+predict(odataset2)
+confint(odataset2)
+baujat(odataset2)
+

### 2024-02-13 scripts/05-replication-table1.R

@@ -1,0 +1,62 @@
+#### Preamble ####
+# Purpose: Replicate Figures and Tables
+# Author: Sami El Sabri, Liban Timir
+# Date: 10 February 2023
+# Contact: sami.elsabri@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(psych)
+library(ggplot2)
+library(knitr)
+
+#### Read data ####
+satisfaction_data <- read_csv("inputs/data/study_1/FW satisfaction-Study 1-data.csv")
+
+# Clean data #
+# satisfaction_data <- satisfaction_data %>% select(freewill, JS, W2JS)
+
+# visualize data #
+
+satisfaction_data_summary <- satisfaction_data %>% summarize(mean_freewill = round(mean(freewill, na.rm = TRUE),2), 
+                                                             mean_js1 = round(mean(JS, na.rm = TRUE),2),
+                                                             mean_js2 = round(mean(W2JS, na.rm = TRUE),2),
+                                                             sd_freewill = round(sd(freewill,  na.rm = TRUE),2),
+                                                             sd_js1 = round(sd(JS, na.rm = TRUE),2),
+                                                             sd_js2 = round(sd(W2JS,  na.rm = TRUE),2))
+
+satisfaction_data_cor_matrix <- cor(satisfaction_data[, c("freewill", "JS", "W2JS")], use = "complete.obs")
+satisfaction_data_cor_matrix <- round(satisfaction_data_cor_matrix, 3)
+# satisfaction_data_cor_matrix <- as.data.frame(satisfaction_data_cor_matrix[lower.tri(satisfaction_data_cor_matrix)])
+
+freewill_items <- satisfaction_data[, c("A11", "A12", "A13", "A14", "A15", "A16", "A17", "A18")]
+alpha_freewill <- alpha(freewill_items)
+alpha_freewill <- alpha_freewill$total$raw_alpha
+alpha_freewill <- round(alpha_freewill,2)
+
+js1_items <- satisfaction_data[, c("G124", "G125", "G126")]
+alpha_js1 <- alpha(js1_items)
+alpha_js1 <- alpha_js1$total$raw_alpha
+alpha_js1 <- round(alpha_js1,2)
+
+js2_items <- satisfaction_data[, c("W2E87", "W2E88", "W2E89")]
[…]

### 2024-02-13 scripts/05-replication.R

@@ -1,19 +1,0 @@
-#### Preamble ####
-# Purpose: Replicate Figures and Tables
-# Author: Sami El Sabri, Liban Timir
-# Date: 10 February 2023
-# Contact: sami.elsabri@mail.utoronto.ca
-# License: MIT
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(haven)
-library(countrycode)
-library(ggplot2)
-
-#### Read data ####
-penn_world_data <- haven::read_dta("inputs/data/data/aggregates/pwt91.dta")
-un_wpp_data <- read_csv("inputs/data/data/aggregates/WPP2019_Period_Indicators_Medium.csv")
-ucdp_data <- haven::read_dta("inputs/data/data/aggregates/ucdp_prio/ucdp-prio-acd-201.dta")
-# cannot access DHS survey data right now but will add later

### 2024-02-13 scripts/07-replication-table3.R

@@ -1,0 +1,60 @@
+#### Preamble ####
+# Purpose: Replicate Table 4 of Feldman et al. (2017)
+# Author: Sami El Sabri, Liban Timir
+# Date: 10 February 2023
+# Contact: sami.elsabri@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(countrycode)
+library(ggplot2)
+library(knitr)
+
+#### Read data ####
+# wvs_data <- read_csv("inputs/data/study_3/WVS_TimeSeries_4_0.csv")
+
+### Clean data
+
+# wvs_data <- wvs_data %>% select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034)
+# 
+# wvs_data <- wvs_data %>% rename(country_code = COUNTRY_ALPHA,
+#                                 year_survey = S020,
+#                                 unified_id = S007,
+#                                 freewill = A173,
+#                                 js = C033,
+#                                 jd = C034
+#                                 )
+# 
+# country_codes <- c("ARG", "BRA", "CHL", "CHN", "CZE", "IND", "JPN", "MEX", "NGA", 
+#                    "POL", "RUS", "SVK", "ZAF", "KOR", "ESP", "CHE", "USA")
+# 
+# wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>% 
+#   filter(freewill > 0)
+
+write_csv(wvs_filtered, 'inputs/data/study_3/wvs_filtered.csv') # because original file is way too big
+
+## Read smaller data file
+wvs_filtered <- read_csv("inputs/data/study_3/wvs_filtered.csv")
+
+wvs_summary_table <- wvs_filtered %>% group_by(country_code) %>% 
+  summarize("FW Mean"=round(mean(freewill),2), n=n())
+
+wvs_filtered_2 <- wvs_filtered %>% filter(js > 0)
+
+correlations <- wvs_filtered_2 %>%
+  group_by(country_code) %>%
+  do(correlation = cor(.$freewill, .$js, use = "complete.obs"))
+
+correlations <- wvs_filtered_2 %>%
+  group_by(country_code) %>%
+  summarize(correlation = list(cor(freewill, js, use = "complete.obs"))) %>%
+  ungroup() %>%
+  mutate(correlation = map_dbl(correlation, ~ round(.x, 2)))
+
[…]

### 2024-02-13 scripts/02-data_cleaning.R
updated scripts

@@ -11,34 +11,22 @@
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+wvs_data <- read_csv("inputs/data/study_3/WVS_TimeSeries_4_0.csv")
+wvs_data <- wvs_data %>% select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034)
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+wvs_data <- wvs_data %>% rename(country_code = COUNTRY_ALPHA,
+                                year_survey = S020,
+                                unified_id = S007,
+                                freewill = A173,
+                                js = C033,
+                                jd = C034
+                                )
+
+country_codes <- c("ARG", "BRA", "CHL", "CHN", "CZE", "IND", "JPN", "MEX", "NGA",
+                   "POL", "RUS", "SVK", "ZAF", "KOR", "ESP", "CHE", "USA")
+
+wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>%
+  filter(freewill > 0)
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_csv(wvs_filtered, 'inputs/data/study_3/wvs_filtered.csv') # because original file is way too big

### 2024-02-13 scripts/07-replication-table3.R

@@ -13,29 +13,6 @@ library(ggplot2)
 library(knitr)
 
 #### Read data ####
-# wvs_data <- read_csv("inputs/data/study_3/WVS_TimeSeries_4_0.csv")
-
-### Clean data
-
-# wvs_data <- wvs_data %>% select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034)
-# 
-# wvs_data <- wvs_data %>% rename(country_code = COUNTRY_ALPHA,
-#                                 year_survey = S020,
-#                                 unified_id = S007,
-#                                 freewill = A173,
-#                                 js = C033,
-#                                 jd = C034
-#                                 )
-# 
-# country_codes <- c("ARG", "BRA", "CHL", "CHN", "CZE", "IND", "JPN", "MEX", "NGA", 
-#                    "POL", "RUS", "SVK", "ZAF", "KOR", "ESP", "CHE", "USA")
-# 
-# wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>% 
-#   filter(freewill > 0)
-
-write_csv(wvs_filtered, 'inputs/data/study_3/wvs_filtered.csv') # because original file is way too big
-
-## Read smaller data file
 wvs_filtered <- read_csv("inputs/data/study_3/wvs_filtered.csv")
 
 wvs_summary_table <- wvs_filtered %>% group_by(country_code) %>% 

### 2024-02-13 outputs/paper/paper.qmd
many edits

@@
 title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
-subtitle: "My subtitle if needed"
+subtitle: "Nowhere near done yet! We had significant issues with our last dataset and had to restart, so bare with us."
 author: 
@@
   - Liban Timir
-thanks: "Code and data are available at: https://github.com/samielsabri/reproduce_paper"
+thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis"
 date: 02-13-2024
@@
 
-install.packages("ggplot2")
-
 library(ggplot2)
 
-gitcreds_set()
 ```
@@
 This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records.
-The dataset underwent meticulous cleaning, addressing missing values and ensuring consistency across responses.
+The dataset underwent meticulous cleaning using R [@citeR], addressing missing values and ensuring consistency across responses.
 Special attention was given to the reliability of scales used for measuring the core variables, with adjustments made to account for the online work setting of the participants.
@@
 
-The precise quantification of child mortality rates captured not only the incidence of deaths but also the timing and causes.
-This entailed using measurement techniques and standard demographic health indicators like the under-five mortality rate (U5MR) or neonatal mortality rate (NMR), which are internationally recognized measures.
-
-Socioeconomic status was gauged using a composite index combining variables such as income, education, and occupation.
-These measurements were tailored to the Moroccan context to accurately reflect local economic conditions and societal structures.
-
-Demographic characteristics were measured using standard metrics such as age, sex, household size, and variables that capture migration or urban-rural residency, given Morocco's diverse landscape from bustling cities to rural areas.
-
-Measurement in this dataset was meticulous to ensure comparability across generations.
-For example, the paper needed to account for changes over time in how mortality or socioeconomic status is recorded and reported within Morocco.
-The potential for measurement error or bias would necessitate rigorous validation techniques, such as cross-referencing with other data sources or conducting field verifications.
-
-The dataset also included constructed variables, which are derived from raw data through transformations or computations to better capture the concepts under study.
-For instance, a constructed variable might be a mortality risk score that combines the number of sibling deaths with the ages at which they occurred.
-
-In the context of Morocco, the discussion of measurement would also address the cultural and linguistic considerations in the data collection process.
-Questionnaires and surveys needed to be accurately translated and culturally adapted to ensure the measurement is valid and reliable across different Moroccan communities.
-
-Incorporating a thorough discussion of measurement in relation to the dataset is essential to validate the paper's findings and to ensure that conclusions drawn are based on accurate and reliable data.
-This discussion would ultimately contribute to the paper's credibility and the robustness of its policy recommendations for Morocco.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
 ```{r}
@@
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```
@@
 
-analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 Talk way more about it.
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("outputs/models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
 
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-02-13 outputs/ssrp_report/ssrp_report.qmd
many edits

---
title: "SSRP Report based on *Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction* by Feldman et al. (2017)
 "
author: Sami El Sabri and Liban Timir
thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis"
date: 02-13-2024
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| echo: false
#| warning: false
#| message: false

#### Loading Packages ####
library(tidyverse)
library(psych)
library(haven)
library(ggplot2)
library(knitr)
library(kableExtra)
library(countrycode)
```

```{r}
#| echo: false
#| warning: false
#| message: false

# Loading the cleaned data
satisfaction_data_taiwan <- read_csv(here::here("inputs/data/study_1/FW satisfaction-Study 1-data.csv"))
satisfaction_data_usa <- read_csv(here::here("inputs/data/study_2/FW satisfaction-Study 2-data.csv"))
wvs_data <- read_csv(here::here("inputs/data/study_3/wvs_filtered.csv"))

```

# Report

Using the R programming language (@citeR) and the tidyverse (@citetidyverse), psych (@citepsych), countrycode (@citecc) and kableExtra (@citeknitr) packages, three figures from *Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction*  by Fraga and Miller (2022) were replicated.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-1
#| tbl-cap: "Replication of Table 1 from Feldman et al. (2017)"

# Clean data for Table 1
satisfaction_data_summary <- satisfaction_data_taiwan %>% summarize(mean_freewill = round(mean(freewill, na.rm = TRUE),2), 
                                                             mean_js1 = round(mean(JS, na.rm = TRUE),2),
                                                             mean_js2 = round(mean(W2JS, na.rm = TRUE),2),
                                                             sd_freewill = round(sd(freewill,  na.rm = TRUE),2),
                                                             sd_js1 = round(sd(JS, na.rm = TRUE),2),
                                                             sd_js2 = round(sd(W2JS,  na.rm = TRUE),2))

satisfaction_data_cor_matrix <- cor(satisfaction_data_taiwan[, c("freewill", "JS", "W2JS")], use = "complete.obs")
satisfaction_data_cor_matrix <- round(satisfaction_data_cor_matrix, 3)

# visualize data #

freewill_items <- satisfaction_data_taiwan[, c("A11", "A12", "A13", "A14", "A15", "A16", "A17", "A18")]
alpha_freewill <- alpha(freewill_items)
alpha_freewill <- alpha_freewill$total$raw_alpha
alpha_freewill <- round(alpha_freewill,2)

js1_items <- satisfaction_data_taiwan[, c("G124", "G125", "G126")]
alpha_js1 <- alpha(js1_items)
alpha_js1 <- alpha_js1$total$raw_alpha
alpha_js1 <- round(alpha_js1,2)

js2_items <- satisfaction_data_taiwan[, c("W2E87", "W2E88", "W2E89")]
alpha_js2 <- alpha(js2_items)
alpha_js2 <- alpha_js2$total$raw_alpha
alpha_js2 <- round(alpha_js2,2)

final_table_study_1 <- data.frame(
  Variable = c("Belief in Free Will (T1)", "Job Satisfaction (T1)", "Job Satisfaction (T2)"),
  Alpha = c(alpha_freewill, alpha_js1, alpha_js2),
  Mean = c(satisfaction_data_summary$mean_freewill, 
           satisfaction_data_summary$mean_js1, 
           satisfaction_data_summary$mean_js2),
  SD = c(satisfaction_data_summary$sd_freewill, 
         satisfaction_data_summary$sd_js1, 
         satisfaction_data_summary$sd_js2),
  'Belief in\nFree Will (T1)' = c(NA, satisfaction_data_cor_matrix[1,2], satisfaction_data_cor_matrix[1,3]),
  "Job\nSatisfaction (T1)" = c(NA, NA, satisfaction_data_cor_matrix[2,3]),
  "Job\nSatisfaction (T2)" = c(NA, NA, NA),
  check.names = FALSE
)

final_table_s1_formatted <- final_table_study_1 %>%
  kable("latex", booktabs = TRUE, escape = FALSE, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>% 
   column_spec(1, width="2cm") %>% 
  column_spec(2, width="2cm") %>% 
   column_spec(3, width="2cm") %>% 
  column_spec(4, width="2cm") %>% 
  column_spec(5, width="2cm") %>% 
  column_spec(6, width="2cm") %>% 
   column_spec(7, width="2cm")

final_table_s1_formatted

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-2
#| tbl-cap: "Replication of Table 2 from Feldman et al. (2017)"

satisfaction_data_usa_summary <- satisfaction_data_usa %>% 
  summarize(
    mean_js1 = round(mean(jobsat1, na.rm = TRUE), 2),
    sd_js1 = round(sd(jobsat1, na.rm = TRUE), 2),
    mean_js2 = round(mean(jobsat2, na.rm = TRUE), 2),
    sd_js2 = round(sd(jobsat2, na.rm = TRUE), 2),
    mean_freewill = round(mean(FWDfwagency, na.rm = TRUE), 2),
    sd_freewill = round(sd(FWDfwagency, na.rm = TRUE), 2),
    mean_jobaut = round(mean(jobaut, na.rm = TRUE), 2),
    sd_jobaut = round(sd(jobaut, na.rm = TRUE), 2),
    mean_jobaut2 = round(mean(jobaut2, na.rm = TRUE), 2),
    sd_jobaut2 = round(sd(jobaut2, na.rm = TRUE), 2),
    mean_locus = round(mean(locus, na.rm = TRUE), 2),
    sd_locus = round(sd(locus, na.rm = TRUE), 2),
    mean_selfcontrol = round(mean(selfcontrol, na.rm = TRUE), 2),
    sd_selfcontrol = round(sd(selfcontrol, na.rm = TRUE), 2),
    mean_selfeff = round(mean(selfeff, na.rm = TRUE), 2),
    sd_selfeff = round(sd(selfeff, na.rm = TRUE), 2),
    mean_selfest = round(mean(selfest, na.rm = TRUE), 2),
    sd_selfest = round(sd(selfest, na.rm = TRUE), 2),
    mean_implicit = round(mean(ess_kind, na.rm = TRUE), 2),
    sd_implicit = round(sd(ess_kind, na.rm = TRUE), 2)
  )

calculate_correlations <- function(data, target_var) {
  # Identify all other variables in the dataset
  other_vars <- setdiff(names(data), target_var)

  # Use map_dfr to iterate over each variable and calculate correlation with target_var
  correlations <- map_dfr(other_vars, function(var) {
    data_subset <- data %>% 
      select(all_of(c(target_var, var))) %>% 
      na.omit()  # Ensure pairwise complete observation

    correlation <- cor(data_subset[[1]], data_subset[[2]], method = "pearson")

    # Return a data frame with the variable name and its correlation with target_var
    tibble(Variable = var, Correlation = correlation)
  })

  return(correlations)
}

# Construct Correlations
satisfaction_data_usa_rel <- satisfaction_data_usa %>% select("jobsat1", "jobsat2", "FWDfwagency", "jobaut",
                                                              "jobaut2", "locus", "ess_kind", "selfest", "selfeff", "selfcontrol")
correlations_jobsat1 <- calculate_correlations(satisfaction_data_usa_rel, "jobsat1")
correlations_jobsat1 <- round(correlations_jobsat1[1:9, 2],2)
correlations_jobsat2 <-  calculate_correlations(satisfaction_data_usa_rel, "jobsat2")
correlations_jobsat2 <- round(correlations_jobsat2[2:9,2],2)
correlations_fw <-  calculate_correlations(satisfaction_data_usa_rel, "FWDfwagency")
correlations_fw <- round(correlations_fw[3:9,2],2)
correlations_jobaut1 <-  calculate_correlations(satisfaction_data_usa_rel, "jobaut")
correlations_jobaut1 <- round(correlations_jobaut1[4:9,2],2)
correlations_jobaut2 <- calculate_correlations(satisfaction_data_usa_rel, "jobaut2")
correlations_jobaut2 <- round(correlations_jobaut2[5:9,2],2)

## Construct Alpha Values
js1_items <- satisfaction_data_usa[, c("jobsat_1", "jobsat_2", "jobsat_3", "jobsat_4", "jobsat_5")]
alpha_js1 <- alpha(js1_items, check.keys = TRUE)
alpha_js1 <- alpha_js1$total$raw_alpha
alpha_js1 <- round(alpha_js1,2)

js2_items <- satisfaction_data_usa[, c("jobsat2_1", "jobsat2_2", "jobsat2_3", "jobsat2_4", "jobsat2_5")]
alpha_js2 <- alpha(js2_items, check.keys = TRUE)
alpha_js2 <- alpha_js2$total$raw_alpha
alpha_js2 <- round(alpha_js2,2)

freewill_items <- satisfaction_data_usa[, c("fw_1", "fw_2", "fw_3", "fw_4", "fw_5", "fw_6", "fw_7", "fw_8", "fw_9")]
alpha_freewill <- alpha(freewill_items)
alpha_freewill <- alpha_freewill$total$raw_alpha
alpha_freewill <- round(alpha_freewill,2)

jaut1_items <- satisfaction_data_usa[, c("jobaut_3", "jobaut_4", "jobaut_5")]
alpha_jaut1 <- alpha(jaut1_items)
alpha_jaut1 <- alpha_jaut1$total$raw_alpha
alpha_jaut1 <- round(alpha_jaut1,2)

jaut2_items <- satisfaction_data_usa[, c("jobaut2_3", "jobaut2_4", "jobaut2_5")]
alpha_jaut2 <- alpha(jaut2_items)
alpha_jaut2 <- alpha_jaut2$total$raw_alpha
alpha_jaut2 <- round(alpha_jaut2,2)

## Construct Final Table
final_table_s2 <- data.frame(
  Variable = c("Job Satisfaction (T1)", "Job Satisfaction (T2)", "Belief in Free Will (T1)",
               "Job Autonomy (T1)", "Job Autonomy (T2)", "Locus of Control", "Implicit Beliefs",
               "Self-Esteem", "Self-Efficacy", "Self-Control"),
  "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2,
                                NA, NA, NA, NA, NA),
  Mean = c(
           satisfaction_data_usa_summary$mean_js1, 
           satisfaction_data_usa_summary$mean_js2,
           satisfaction_data_usa_summary$mean_freewill,
           satisfaction_data_usa_summary$mean_jobaut,
           satisfaction_data_usa_summary$mean_jobaut2,
           satisfaction_data_usa_summary$mean_locus,
           satisfaction_data_usa_summary$mean_implicit,
           satisfaction_data_usa_summary$mean_selfest,
           satisfaction_data_usa_summary$mean_selfeff,
           satisfaction_data_usa_summary$mean_selfcontrol),
  SD = c(satisfaction_data_usa_summary$sd_js1, 
         satisfaction_data_usa_summary$sd_js2,
         satisfaction_data_usa_summary$sd_freewill, 
         satisfaction_data_usa_summary$sd_jobaut,
         satisfaction_data_usa_summary$sd_jobaut2,
         satisfaction_data_usa_summary$sd_locus,
         satisfaction_data_usa_summary$sd_implicit,
         satisfaction_data_usa_summary$sd_selfest,
         satisfaction_data_usa_summary$sd_selfeff,
         satisfaction_data_usa_summary$sd_selfcontrol),
  "Job Satisfaction (T1)" = c(NA, 
                              correlations_jobsat1[[1,1]],
                              correlations_jobsat1[[2,1]],
                              correlations_jobsat1[[3,1]],
                              correlations_jobsat1[[4,1]],
                              correlations_jobsat1[[5,1]],
                              correlations_jobsat1[[6,1]],
                              correlations_jobsat1[[7,1]],
                              correlations_jobsat1[[8,1]],
                              correlations_jobsat1[[9,1]]),
  "Job Satisfaction (T2)" = c(NA, NA,
                              correlations_jobsat2[[1,1]],
                              correlations_jobsat2[[2,1]],
                              correlations_jobsat2[[3,1]],
                              correlations_jobsat2[[4,1]],
                              correlations_jobsat2[[5,1]],
                              correlations_jobsat2[[6,1]],
                              correlations_jobsat2[[7,1]],
                              correlations_jobsat2[[8,1]]),
  "Belief in Free Will (T1)" = c(NA, NA, NA,
                                 correlations_fw[[1,1]],
                                 correlations_fw[[2,1]],
                                 correlations_fw[[3,1]],
                                 correlations_fw[[4,1]],
                                 correlations_fw[[5,1]],
                                 correlations_fw[[6,1]],
                                 correlations_fw[[7,1]]),

  "Job Autonomy (T1)" = c(NA, NA, NA, NA,
                          correlations_jobaut1[[1,1]],
                          correlations_jobaut1[[2,1]],
                          correlations_jobaut1[[3,1]],
                          correlations_jobaut1[[4,1]],
                          correlations_jobaut1[[5,1]],
                          correlations_jobaut1[[6,1]]),

   "Job Autonomy (T2)" = c(NA, NA, NA, NA, NA,
                           correlations_jobaut1[[1,1]],
                           correlations_jobaut1[[2,1]],
                           correlations_jobaut1[[3,1]],
                           correlations_jobaut1[[4,1]],
                          correlations_jobaut2[[5,1]]),

  check.names = FALSE
)
final_table_s2_formatted <- final_table_s2 %>%
kable("latex", booktabs = TRUE, escape = FALSE, linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>% 
    column_spec(1, width="2cm") %>% 
  column_spec(2, width="1.5cm") %>% 
   column_spec(3, width="0.5cm") %>% 
  column_spec(4, width="0.5cm") %>% 
  column_spec(5, width="1.5cm") %>% 
  column_spec(6, width="1.5cm") %>% 
   column_spec(7, width="1.5cm") %>% 
  column_spec(8, width="1.5cm")

final_table_s2_formatted

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-3
#| tbl-cap: "Replication of Table 4 from Feldman et al. (2017)"

#### Read data ####

wvs_summary_table <- wvs_data %>% group_by(country_code) %>% 
  summarize("FW Mean"=round(mean(freewill),2), n=n())

wvs_filtered_2 <- wvs_data %>% filter(js > 0)

correlations <- wvs_filtered_2 %>%
  group_by(country_code) %>%
  do(correlation = cor(.$freewill, .$js, use = "complete.obs"))

correlations <- wvs_filtered_2 %>%
  group_by(country_code) %>%
  summarize(correlation = list(cor(freewill, js, use = "complete.obs"))) %>%
  ungroup() %>%
  mutate(correlation = map_dbl(correlation, ~ round(.x, 2)))

final_table <- left_join(wvs_summary_table, correlations, by = "country_code")
final_table <- final_table %>% mutate("Country Name" = countrycode(country_code, "iso3c", "country.name"))
final_table <- final_table[c(5, 2, 4, 3)]
final_table <- final_table %>% rename("Correlation" = correlation)
final_table <- final_table %>% filter(`Country Name` != 'United States')

final_table_wvs_formatted <- final_table %>% kable("latex", booktabs = TRUE, escape = FALSE, linesep = "") %>% kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)

final_table_wvs_formatted
```

@tbl-1, @tbl-2, and @tbl-3 suggest that the reproduction of these figures from Feldman et al. (2017) was successful.

\newpage
# References

### 2024-02-13 scripts/01-download_data.R

@@ -1,26 +1,22 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data necessary
+# Authors: Sami El Sabri, Liban Timir
+# Date: 10 February 2023
+# Contact: sami.elsabri@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Download 1.3GB large file titled 'WVS TimeSeries 1981 2022 Csv v4 0.zip' from 
+# https://www.worldvaluessurvey.org/WVSDocumentationWVL.jsp
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
+
+# wvs_data <- read_csv("inputs/data/study_3/WVS_TimeSeries_4_0.csv")
+# This file is too big to add to this folder and to github. 
+# Follow above instructions and add the file to the specified filepath
 
 
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 
          

### 2024-02-13 scripts/02-data_cleaning.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data provided by Feldman et al. (2017) and by WVS
+# Authors: Sami El Sabri, Liban Timir
+# Date: 10 February 2023
+# Contact: sami.elsabri@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data.R
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-02-13 scripts/05-replication-table1.R

@@ -1,6 +1,6 @@
 #### Preamble ####
-# Purpose: Replicate Figures and Tables
-# Author: Sami El Sabri, Liban Timir
+# Purpose: Replicate Table 1 of Feldman et al. (2017)
+# Authors: Sami El Sabri, Liban Timir
 # Date: 10 February 2023
 # Contact: sami.elsabri@mail.utoronto.ca
 # License: MIT
@@ -11,14 +11,13 @@ library(tidyverse)
 library(psych)
 library(ggplot2)
 library(knitr)
+library(haven)
 
 #### Read data ####
 satisfaction_data <- read_csv("inputs/data/study_1/FW satisfaction-Study 1-data.csv")
 
 # Clean data #
-# satisfaction_data <- satisfaction_data %>% select(freewill, JS, W2JS)
 
-# visualize data #
 
 satisfaction_data_summary <- satisfaction_data %>% summarize(mean_freewill = round(mean(freewill, na.rm = TRUE),2), 
                                                              mean_js1 = round(mean(JS, na.rm = TRUE),2),
@@ -29,7 +28,8 @@ satisfaction_data_summary <- satisfaction_data %>% summarize(mean_freewill = rou
 
 satisfaction_data_cor_matrix <- cor(satisfaction_data[, c("freewill", "JS", "W2JS")], use = "complete.obs")
 satisfaction_data_cor_matrix <- round(satisfaction_data_cor_matrix, 3)
-# satisfaction_data_cor_matrix <- as.data.frame(satisfaction_data_cor_matrix[lower.tri(satisfaction_data_cor_matrix)])
+
+# visualize data #
 
 freewill_items <- satisfaction_data[, c("A11", "A12", "A13", "A14", "A15", "A16", "A17", "A18")]
 alpha_freewill <- alpha(freewill_items)
@@ -46,7 +46,7 @@ alpha_js2 <- alpha(js2_items)
 alpha_js2 <- alpha_js2$total$raw_alpha
 alpha_js2 <- round(alpha_js2,2)
 
-final_table <- data.frame(
+final_table_study_1 <- data.frame(
   Variable = c("Belief in Free Will (T1)", "Job Satisfaction (T1)", "Job Satisfaction (T2)"),
   "Reliability Coefficient" = c(alpha_freewill, alpha_js1, alpha_js2),
   Mean = c(satisfaction_data_summary$mean_freewill, 

### 2024-02-14 outputs/paper/paper.qmd
wrote intro

@@
   - Liban Timir
-thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis"
+thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis.
+SSRP replication available at: https://www.socialsciencereproduction.org/reproductions/94caaeaf-7e11-4efa-9269-7729fc2e0837/index"
 date: 02-13-2024

### 2024-02-14 outputs/paper/paper.qmd
data section outline

@@
 # Introduction
-In the evolving landscape of organizational psychology, the exploration of individual agency beliefs (particularly free will) and their impact on job satisfaction presents a compelling field of study.
-"Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction" by Feldman et al.
-embarks on this journey, unveiling the nuanced relationship between one's belief in free will and their subsequent job satisfaction across diverse cultural contexts.
-A focused exploration of this relationship within the context of the American workforce provides a valuable estimand, given the United States' strong emphasis on individualism, autonomy, and the freedom to shape one's destiny which are principles deeply ingrained in the national ethos.
 
-The paper addresses a significant gap in existing literature by articulating how free will beliefs, beyond serving as philosophical contemplations, exert a tangible influence on individuals' professional lives.
-Through a robust approach that includes longitudinal studies and cross-cultural analyses, the research highlights a consistent positive correlation between strong beliefs in free will and higher levels of job satisfaction.
-This relationship, significantly influenced by perceived autonomy, underscores the pivotal role of individual agency beliefs in the context of the American workplace, where personal freedom and self-determination are highly valued.
+In recent years, the intersection between personal beliefs in free will and cognitive behavioral outcomes has emerged as a pivotal area of psychological inquiry.
+While the existence of free will is a highly theoretical and philosophical question, the belief in free will has undeniable effects on various other psychological constructs such as autonomy, meaningfulness, and self-efficacy (@baumeister2014, @alquist2013).
+Despite the robustness of these relationships, there remain gaps in the literature of the specific dynamics of these effects and the generalizability in field settings.
+@feldman2017 conducted a study investigating the effects of the belief in free will on job satisfaction and attempted to draw cross-cultural and longitudinal conclusions on the positive correlation between the belief in free will and job satisfaction.
 
-The importance of this paper lies not only in its findings but also in its implications, offering practical insights for enhancing organizational culture and employee satisfaction within the American context.
-By highlighting the importance of fostering environments that champion autonomy and respect individual agency beliefs, the paper prompts business leaders and policymakers to rethink strategies for workplace management and development.
+They executed three distinct studies: the first with real estate agents in Taiwan over three months, the second involving American workers over six months using Amazon Mechanical Turk, and the third utilizing a large cross-cultural sample from the World Values Survey encompassing 16 countries.
+This multifaceted approach allowed them to assess the generalizability of free will beliefs as predictors of job satisfaction across various cultural contexts and professional environments, providing a robust examination of how these beliefs influence job satisfaction over time.
+
+Utilizing the same dataset and a similar methodology to Feldman et al.
+(2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality.
+While Feldman et al.
+did investigate the relationship between the belief in free will and job satisfaction in the United States, they did not integrate these results to the cross-cultural analysis, as the US were not included in the sample of 16 countries.
+This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al.
+paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey.
+The estimand is the correlation between the belief in free will and job satisfaction.
+Our reproduction was conducted using the statistical programming language R (@citeR).
+In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc).
+
+We begin our paper with a closer look at the data source and measurement (@sec-data), followed by a selection of relevant results (@sec-results).
+Finally, we will conclude with a discussion of our findings to integrate our replication with the original paper by @feldman2017 and the broader literature on free will beliefs.
+We will also discuss potential ethical biases, limitations, and future directions.
 This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.
-
-Structurally, the paper unfolds starting from its comprehensive methodology (including the six-month study of American online workers) to its extensive cross-cultural survey, which contextualizes the American data within a global framework.
-It then articulates the specific implications of free will beliefs for job satisfaction among American employees, weaving these insights into broader discussions on the interplay between cultural values, individual beliefs, and workplace dynamics.
-The concluding sections propose future research directions and practical applications, emphasizing the critical role of understanding and leveraging individual agency beliefs in cultivating a more motivated and satisfied workforce.
-
-You can and should cross-reference sections and sub-sections.
-
-The remainder of this paper is structured as follows. @sec-data....
+### TALK ABOUT FINDINGS HERE###
 
 # Data {#sec-data}
+## Source {#sec-source}
+Dataset Overview:
+
+Introduction to the Dataset: Start by providing a brief overview of the dataset(s) used, including the source (e.g., Amazon Mechanical Turk, World Values Survey) and the rationale for selecting these datasets for replication.
+Scope and Scale: Mention the size of the dataset, the number of participants, and the time frame covered by the data collection.
+## Measurement {#sec-measurement}
+Variables Description:
+
+Dependent Variable(s): Describe the main variable of interest, job satisfaction, including how it was measured or operationalized in the dataset.
+Independent Variable(s): Explain the measurement of free will beliefs and any other relevant variables that were analyzed as predictors or controls in the study (e.g. job autonomy, self-efficacy etc.)
+
+Covariates and Controls: If applicable, detail any additional variables used as controls or covariates in your analysis, such as demographic information, employment characteristics, or cultural factors.
+
+GO INTO GREAT DETAIL WITH MEASUREMENT!
+
+## Data Characteristics {#sec-characteristics}
+
+Preprocessing Steps: Outline the steps taken to prepare the data for analysis, including any cleaning, filtering, or transformation processes.
+Handling of Missing Data: Describe how missing data were addressed, whether through imputation, exclusion, or another method.
+
+Summary Statistics and Initial Observations:
+
+Descriptive Statistics: Provide summary statistics for the main variables, including means, standard deviations, and ranges.
+This gives readers a sense of the data's central tendencies and variability.
+Visualizations: Include graphs or tables that offer an initial view of the data, such as distributions of job satisfaction and free will beliefs.
+Discuss any notable patterns or preliminary observations.
+Comparative Analysis (if applicable):
+
+Comparison with Original Study: If you have access to summary statistics or data visualizations from the Feldman et al.
+study, briefly compare those findings with your dataset to highlight similarities or differences.
+Rationale for Differences: Discuss any expected or surprising differences in the data between the original study and your replication effort, potentially attributable to cultural or temporal differences.
+
+#####
 

### 2024-02-14 outputs/paper/paper.qmd
some more edits

@@
 paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey.
+We will also consider whether there are any significant differences between the national-level data and the Amazon Mechanical Turk data.
 The estimand is the correlation between the belief in free will and job satisfaction.
@@
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-```
-
-Talk way more about it.
+# Results {#sec-results}
+A173 free will
+c033 job satisfaction
+c034 decisions in the job
+F198 Fate versus control
+G023 autonomous individual
+C031 degree of pride in your work
+X003 Age
+X001 Sex
 

### 2024-02-14 outputs/paper/paper.qmd
started results section

@@
 library(ggplot2)
+library(MASS)
+library(tidyverse)
+library(car)
+library(psych)
+library(knitr)
+library(kableExtra)
+library(corrplot)
+
+wvs_data_usa <- read_csv(here::here('outputs/data/wvs_data_usa.csv'))
+satisfaction_data_usa <- read_csv(here::here('inputs/data/study_2/FW satisfaction-Study 2-data.csv'))
+satisfaction_data_usa_rel <- read_csv(here::here('outputs/data/satisfaction_data_usa_rel.csv'))
 
@@
 
+In order to assess the internal validity and reliability of the psychological constructs measured in @feldman2017, we verified the Cronbach-Alpha reliability coefficients based on the raw dataset.
+As shown in @tbl-reliability, we were able to successfully replicate the coefficients for most constructs.
+The only deviation is with the trait locus of control, which has a coefficient α = .58 in @rotter1966, but 0.61 in our replication, indicating even greater confidence that the survey questions indeed measure the underlying construct.
+
+```{r, include=FALSE, message=FALSE, echo=FALSE}
+js1_items <- satisfaction_data_usa[, c("jobsat_1", "jobsat_2", "jobsat_3", "jobsat_4", "jobsat_5")]
+alpha_js1 <- alpha(js1_items)
+alpha_js1 <- alpha_js1$total$raw_alpha
+alpha_js1 <- round(alpha_js1,2)
+
+js2_items <- satisfaction_data_usa[, c("jobsat2_1", "jobsat2_2", "jobsat2_3", "jobsat2_4", "jobsat2_5")]
+alpha_js2 <- alpha(js2_items)
+alpha_js2 <- alpha_js2$total$raw_alpha
+alpha_js2 <- round(alpha_js2,2)
+
+freewill_items <- satisfaction_data_usa[, c("fw_1", "fw_2", "fw_3", "fw_4", "fw_5", "fw_6", "fw_7", "fw_8", "fw_9")]
+alpha_freewill <- alpha(freewill_items)
+alpha_freewill <- alpha_freewill$total$raw_alpha
+alpha_freewill <- round(alpha_freewill,2)
+
+jaut1_items <- satisfaction_data_usa[, c("jobaut_3", "jobaut_4", "jobaut_5")]
+alpha_jaut1 <- alpha(jaut1_items)
+alpha_jaut1 <- alpha_jaut1$total$raw_alpha
+alpha_jaut1 <- round(alpha_jaut1,2)
+
+jaut2_items <- satisfaction_data_usa[, c("jobaut2_3", "jobaut2_4", "jobaut2_5")]
+alpha_jaut2 <- alpha(jaut2_items)
+alpha_jaut2 <- alpha_jaut2$total$raw_alpha
+alpha_jaut2 <- round(alpha_jaut2,2)
+
+locus_items <- satisfaction_data_usa[, c("lc1", "lc2", "lc3", "lc4", "lc5", "lc6", "lc7", "lc8", "lc9", "lc10", "lc11", "lc12", "lc13")]
+alpha_locus <- alpha(locus_items, check.keys=TRUE)
+alpha_locus <- alpha_locus$total$raw_alpha
+alpha_locus <- round(alpha_locus,2)
+
+self_eff_items <- satisfaction_data_usa[, c("selfeff_1", "selfeff_2", "selfeff_3")]
+alpha_self_eff <- alpha(self_eff_items)
+alpha_self_eff <- alpha_self_eff$total$raw_alpha
+alpha_self_eff <- round(alpha_self_eff,2)
+
+self_est_items <- satisfaction_data_usa[, c("selfest_1", "selfest_2", "selfest_3", "selfest_4", "selfest_5", "selfest_6", "selfest_7", "selfest_8", "selfest_9", "selfest_10")]
+alpha_self_est <- alpha(self_est_items, check.keys=TRUE)
+alpha_self_est <- alpha_self_est$total$raw_alpha
+alpha_self_est <- round(alpha_self_est,2)
+
+self_con_items <- satisfaction_data_usa[, c("selfcon_1", "selfcon_2", "selfcon_3", "selfcon_4", "selfcon_5", "selfcon_6", "selfcon_7", "selfcon_8", "selfcon_9", "selfcon_10", "selfcon_11", "selfcon_12", "selfcon_13")]
+alpha_self_con <- alpha(self_con_items, check.keys=TRUE)
+alpha_self_con <- alpha_self_con$total$raw_alpha
+alpha_self_con <- round(alpha_self_con,2)
+
+implicit_items <- satisfaction_data_usa[, c("lay_1", "lay_2", "lay_3", "lay_4", "lay_5r", "lay_6r", "lay_7r", "lay_8r")]
+alpha_implicit <- alpha(implicit_items, check.keys=TRUE)
+alpha_implicit <- alpha_implicit$total$raw_alpha
+alpha_implicit <- round(alpha_implicit,2)
+
+reliability_scores <- data.frame(
+  Rows = c("Job Satisfaction (T1)", "Job Satisfaction (T2)", "Belief in Free Will (T1)", 
+           "Job Autonomy (T1)", "Job Autonomy (T2)", "Locus of Control", 
+           "Implicit Beliefs", "Self-Esteem", "Self-Efficacy", "Self-Control"),
+  "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2, alpha_locus, alpha_self_eff, alpha_self_est, alpha_implicit, alpha_self_con)
+)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-reliability
+#| tbl-cap: Cronbach Alpha Reliability Coefficients for Psychological Constructs measured in Feldman et al. (2017)
+
+kable(reliability_scores)
+```
+
 ## Data Characteristics {#sec-characteristics}
+The original research survey data published by @feldman2017 did not require any further data cleaning.
+Using the aforementioned constructs which are derived from their respective set of survey questions, we were able to replicate all the means and standard deviations, as seen in @tbl-st2summary.
 
-Preprocessing Steps: Outline the steps taken to prepare the data for analysis, including any cleaning, filtering, or transformation processes.
-Handling of Missing Data: Describe how missing data were addressed, whether through imputation, exclusion, or another method.
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-st2summary
+#| tbl-cap: Summary Statistics for Psychological Constructs measured in Feldman et al. (2017)
+
+satisfaction_data_usa_summary <- satisfaction_data_usa %>% 
+  summarize(
+    mean_age = round(mean(age),2),
+    sd_age = round(sd(age),2),
+    mean_js1 = round(mean(jobsat1, na.rm = TRUE), 2),
+    sd_js1 = round(sd(jobsat1, na.rm = TRUE), 2),
+    mean_js2 = round(mean(jobsat2, na.rm = TRUE), 2),
+    sd_js2 = round(sd(jobsat2, na.rm = TRUE), 2),
+    mean_freewill = round(mean(FWDfwagency, na.rm = TRUE), 2),
+    sd_freewill = round(sd(FWDfwagency, na.rm = TRUE), 2),
+    mean_jobaut = round(mean(jobaut, na.rm = TRUE), 2),
+    sd_jobaut = round(sd(jobaut, na.rm = TRUE), 2),
+    mean_jobaut2 = round(mean(jobaut2, na.rm = TRUE), 2),
+    sd_jobaut2 = round(sd(jobaut2, na.rm = TRUE), 2),
+    mean_locus = round(mean(locus, na.rm = TRUE), 2),
+    sd_locus = round(sd(locus, na.rm = TRUE), 2),
+    mean_selfcontrol = round(mean(selfcontrol, na.rm = TRUE), 2),
+    sd_selfcontrol = round(sd(selfcontrol, na.rm = TRUE), 2),
+    mean_selfeff = round(mean(selfeff, na.rm = TRUE), 2),
+    sd_selfeff = round(sd(selfeff, na.rm = TRUE), 2),
+    mean_selfest = round(mean(selfest, na.rm = TRUE), 2),
+    sd_selfest = round(sd(selfest, na.rm = TRUE), 2),
+    mean_implicit = round(mean(ess_kind, na.rm = TRUE), 2),
+    sd_implicit = round(sd(ess_kind, na.rm = TRUE), 2)
+  )
+
+satisfaction_data_usa_summary <- data.frame(
+  Variable = c("Age", "Job Satisfaction (T1)", "Job Satisfaction (T2)", "Belief in Free Will (T1)",
+               "Job Autonomy (T1)", "Job Autonomy (T2)", "Locus of Control", "Implicit Beliefs",
+               "Self-Esteem", "Self-Efficacy", "Self-Control"),
+  Mean = c(
+          satisfaction_data_usa_summary$mean_age,
+           satisfaction_data_usa_summary$mean_js1, 
+           satisfaction_data_usa_summary$mean_js2,
+           satisfaction_data_usa_summary$mean_freewill,
+           satisfaction_data_usa_summary$mean_jobaut,
+           satisfaction_data_usa_summary$mean_jobaut2,
+           satisfaction_data_usa_summary$mean_locus,
+           satisfaction_data_usa_summary$mean_implicit,
+           satisfaction_data_usa_summary$mean_selfest,
+           satisfaction_data_usa_summary$mean_selfeff,
+           satisfaction_data_usa_summary$mean_selfcontrol),
+  SD = c(satisfaction_data_usa_summary$sd_age,
+        satisfaction_data_usa_summary$sd_js1, 
+         satisfaction_data_usa_summary$sd_js2,
+         satisfaction_data_usa_summary$sd_freewill, 
+         satisfaction_data_usa_summary$sd_jobaut,
+         satisfaction_data_usa_summary$sd_jobaut2,
+         satisfaction_data_usa_summary$sd_locus,
+         satisfaction_data_usa_summary$sd_implicit,
+         satisfaction_data_usa_summary$sd_selfest,
+         satisfaction_data_usa_summary$sd_selfeff,
+         satisfaction_data_usa_summary$sd_selfcontrol))
+
+kable(satisfaction_data_usa_summary)
+```
+
+The World Values Survey dataset needed some additional cleaning steps, filtering for certain variables of interest and only for surveys based in the United States of America.
+See @tbl-wvssummary for summary statistics of selected psychological constructs.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-wvssummary
+#| tbl-cap: Summary Statistics for selected Psychological Constructs measured in the World Values Survey USA, 1981-2017
+
+wvs_data_usa_summary <- wvs_data_usa %>% summarise(
+  mean_age = round(mean(Age, na.rm = TRUE),2),
+    sd_age = round(sd(Age, na.rm = TRUE),2),
+  mean_freewill = round(mean(freewill, na.rm = TRUE),2),
+  sd_freewill = round(sd(freewill, na.rm = TRUE),2),
+  mean_js = round(mean(job_satisfaction, na.rm = TRUE),2),
+  sd_js = round(sd(job_satisfaction, na.rm = TRUE),2),
+  mean_jaut = round(mean(job_decision, na.rm = TRUE),2),
+  sd_jaut = round(sd(job_decision, na.rm = TRUE),2),
+  mean_fate = round(mean(fate, na.rm = TRUE),2),
+  sd_fate = round(sd(fate, na.rm = TRUE),2),
+  mean_pride = round(mean(job_pride, na.rm = TRUE),2),
+  sd_pride= round(sd(job_pride, na.rm = TRUE),2),
+  mean_autonomy = round(mean(autonomy, na.rm = TRUE),2),
+  sd_autonomy = round(sd(autonomy, na.rm = TRUE),2))
+
+wvs_data_usa_summary <- data.frame(
+  Variable = c("Age","Belief in Free Will", "Job Satisfaction", 
+               "Job Autonomy", "Job Pride", "Fate vs. Control", "Personal Autonomy"),
+  Mean = c(wvs_data_usa_summary$mean_age,
+           wvs_data_usa_summary$mean_freewill,
+           wvs_data_usa_summary$mean_js,
+           wvs_data_usa_summary$mean_jaut,
+           wvs_data_usa_summary$mean_pride,
+           wvs_data_usa_summary$mean_fate,
+           wvs_data_usa_summary$mean_autonomy),
+  SD = c(wvs_data_usa_summary$sd_age,
+         wvs_data_usa_summary$sd_freewill,
+         wvs_data_usa_summary$sd_js,
+         wvs_data_usa_summary$sd_jaut,
+         wvs_data_usa_summary$sd_pride,
+         wvs_data_usa_summary$sd_fate,
+         wvs_data_usa_summary$sd_autonomy))
+
+wvs_data_usa_summary
+
+```
 
@@
 
-#####
+# Results {#sec-results}
+## Amazon Mechanical Turk Sample
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-corst2
+#| fig-cap: Correlation Matrix for Psychological Constructs measured in Study 2 of Feldman et al. (2017)
+#| fig-width: 10
+#| fig-height: 10
 
-The dataset for the study provides a detailed snapshot of free will beliefs, job satisfaction, and perceived job autonomy among American online workers.
+satisfaction_data_usa_rel_num <- satisfaction_data_usa_rel %>% dplyr::select(-Age, -Sex, -age_group)
+cor_matrix <- cor(satisfaction_data_usa_rel_num, use = 'pairwise.complete.obs')
 
-The variables within this dataset were carefully selected to reflect key indicators of job satisfaction, belief in free will, job autonomy, and additional agency constructs for regional analysis within America.
+# Now, cor_matrix contains your full correlation matrix
+corrplot(cor_matrix, method = "circle", type='full', tl.col="black", sig.level = 0.05, insig = "blank")
 
-Data cleaning was especially important in this case, considering the challenges inherent in longitudinal and generational health data.
-This ensured the integrity and continuity of data across different time points and handling any missing or inconsistent records.
-The dataset underwent meticulous cleaning using R [@citeR], addressing missing values and ensuring consistency across responses.
-Special attention was given to the reliability of scales used for measuring the core variables, with adjustments made to account for the online work setting of the participants.
+cor_fw_js1 <- cor.test(satisfaction_data_usa_rel$`Belief in Free Will (T1)`, 
+                   satisfaction_data_usa_rel$`Job Satisfaction (T1)`, method = "pearson")
 
-Summary statistics revealed the mean and median job satisfaction rates, the correlation in job autonomy, and other job-related metrics.
-This aggregated data provided a foundation for understanding the base conditions of the workplace and any preliminary patterns indicating the persistence of individual agency.
+cor_fw_js1_correlation_coefficient <- round(cor_fw_js1$estimate,2)
+cor_fw_js1_p_value <- cor_fw_js1$p.value
+cor_fw_js1_ci <- round(cor_fw_js1$conf.int,2)
 
-Visual representations, such as graphs and tables, illustrated the distribution of job satisfaction, free will beliefs, and the relationship between the two.
-These visuals helped to convey the depth and nuances of the autonomy persistence observed in the American data.
+cor_fw_js2 <- cor.test(satisfaction_data_usa_rel$`Belief in Free Will (T1)`, 
+                   satisfaction_data_usa_rel$`Job Satisfaction (T2)`, method = "pearson")
 
-The appendices include detailed statistical tables, additional graphs showing complex data relationships, and extensive notes on the data cleaning and processing methodology.
+cor_fw_js2_correlation_coefficient <- round(cor_fw_js2$estimate,2)
+cor_fw_js2_p_value <- cor_fw_js2$p.value
+cor_fw_js2_ci <- round(cor_fw_js2$conf.int,2)
 
-This description of the dataset was written with the general ethical practices of demographic research in mind and provides a narrative for a subset of data focused on America.
+cor_fw_jaut1 <- cor.test(satisfaction_data_usa_rel$`Belief in Free Will (T1)`, 
+                   satisfaction_data_usa_rel$`Job Autonomy (T1)`, method = "pearson")
 
-# Results {#sec-results}
-A173 free will
-c033 job satisfaction
-c034 decisions in the job
-F198 Fate versus control
-G023 autonomous individual
-C031 degree of pride in your work
-X003 Age
-X001 Sex
+cor_fw_jaut1_correlation_coefficient <- round(cor_fw_jaut1$estimate,2)
+cor_fw_jaut1_p_value <- cor_fw_jaut1$p.value
+cor_fw_jaut1_ci <- round(cor_fw_jaut1$conf.int,2)
+```
+In exploring free will beliefs and their impact on job satifaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends Feldman et al.'s results.
+As seen in @fig-corst2, most variables are significantly correlated with each other, with the highest correlations being unsurprisingly between the two measurements of Job satisfaction.
+Locus of control lacks any significant correlations, which together with its low reliability coefficient designates it as a less decisive control variable.
+The most important relationship, however, is between free will beliefs and job satisfaction: The belief in free will was significantly positively correlated with job satisfaction both at Time 1 (*r* = `r cor_fw_js1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`]) and at Time 2 ( (r = `r cor_fw_js2_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js2_ci[1]`, `r cor_fw_js1_ci[2]`])).
+However, this correlation is not as strong as the one between free will beliefs and job autonomy (*r* = `r cor_fw_jaut1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_jaut1_ci[1]`, `r cor_fw_jaut1_ci[2]`]).
+This supports the claim that job autonomy may be the most important mediating variable between free will beliefs and job satisfaction.
+Moreover, a step-wise multiple regression on job satisfaction with all psychological agency constructs (full results in @sec-apx-stepwise) confirmed that the effect of free will beliefs on job satisfaction is robust and the strongest relative impact, even when controlling for other agency constructs (Time 1: *p* < 0.034; Time 2: *p* < 0.031).
+
+The replication of study 2 of @feldman2017 supports the claim that there is a direct positive correlation between the belief in free will and job satisfaction over time and controlling for other psychological agency constructs.
+
+### Demographic Factors
+@fig-ageboxplotst2 shows that there are slight differences in the median belief in free will among the age groups.
+However, these differences were not found to be statistically significant, as shown using ANOVA (*F*(4, 204) = 1.886, *p* = .114), even when collapsing individuals over 50 into one age group (*F*(3, 205) = 2.08, *p* = .257).
+Similarly, using linear regression with Age Group as an interaction term, we do not observe a significant effect of age on the relationship between the belief in free will and job satisfaction.
+
+Looking at sex (@fig-sexboxplotst2), on the other hand, we observe a significant difference in the belief in free will, with women having on average higher ratings of believing in free will (*p* < 0.05).
+However, the effect of sex on the relationship between free will beliefs and job satisfaction has not been found to be significant (*p* = 0.58).
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-ageboxplotst2
+#| fig-cap: Belief in free will among US-American Amazon Mechanical Turk Workers by Age Group
+
+ggplot(satisfaction_data_usa_rel, aes(x = age_group, y = `Belief in Free Will (T1)`)) +
+  geom_boxplot(fill = "lightblue") +
+  labs(
+       x = "Age Group",
+       y = "Belief in Free Will") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  + theme_minimal()
+```
+
+```{r, include=FALSE, echo=FALSE}
+leveneTest(`Belief in Free Will (T1)` ~ age_group, data = satisfaction_data_usa_rel) # assumption met because p-value is 0.08
+
+anova_result <- aov(`Belief in Free Will (T1)` ~ age_group, data = satisfaction_data_usa_rel)
+summary(anova_result)
+model <- lm(`Job Satisfaction (T1)`~ `Belief in Free Will (T1)` * age_group, data = satisfaction_data_usa_rel)
+summary(model)
+t.test(`Belief in Free Will (T1)` ~ Sex, data = satisfaction_data_usa_rel)
+
+lm_interaction <- lm(`Job Satisfaction (T1)` ~ `Belief in Free Will (T1)` * factor(Sex), data = satisfaction_data_usa_rel)
+summary(lm_interaction)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-sexboxplotst2
+#| fig-cap: Belief in free will among US-American Amazon Mechanical Turk Workers by Sex
+
+ggplot(satisfaction_data_usa_rel, aes(x = factor(Sex, labels = c("Male", "Female")), y = `Belief in Free Will (T1)`)) +
+  geom_boxplot(fill = "lightblue") +
+  labs(
+       x = "Sex",
+       y = "Belief in Free Will") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  + theme_minimal()
+
+```
+
+## National Sample (WVS)
 
@@
 
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+# Appendix {sec-appendix}
+## Step-Wise regression results {sec-apx-stepwise}
 
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+full_model_t1 <- lm(`Job Satisfaction (T1)` ~ `Belief in Free Will (T1)` + `Self-Esteem` + `Self-Efficacy` + `Self-Control` + `Locus of Control` + `Implicit Beliefs`, data = satisfaction_data_usa_rel)
+
+# Perform stepwise regression using AIC as the criterion
+step_model_t1 <- stepAIC(full_model_t1, direction = "both", trace = FALSE)
+
+# Summary of the final model to get coefficients, R-squared, ANOVA, and confidence intervals
+summary(step_model_t1)
+
+# ANOVA table for the model
+anova(step_model_t1)
+
+# Confidence intervals for the model coefficients
+confint(step_model_t1, level = 0.95)
+
+full_model_t2 <- lm(`Job Satisfaction (T2)` ~ `Belief in Free Will (T1)` + `Self-Esteem` + `Self-Efficacy` + `Self-Control` + `Locus of Control` + `Implicit Beliefs`, data = satisfaction_data_usa_rel)
+
+# Perform stepwise regression using AIC as the criterion
+step_model_t2 <- stepAIC(full_model_t2, direction = "both", trace = FALSE)
+
+# Summary of the final model to get coefficients, R-squared, ANOVA, and confidence intervals
+summary(step_model_t2)
+
+# ANOVA table for the model
+anova(step_model_t2)
+
+# Confidence intervals for the model coefficients
+confint(step_model_t2, level = 0.95)
 

### 2024-02-14 outputs/ssrp_report/ssrp_report.qmd
started results section

@@
 
+locus_items <- satisfaction_data_usa[, c("lc1", "lc2", "lc3", "lc4", "lc5", "lc6", "lc7", "lc8", "lc9", "lc10", "lc11", "lc12", "lc13")]
+alpha_locus <- alpha(locus_items, check.keys=TRUE)
+alpha_locus <- alpha_locus$total$raw_alpha
+alpha_locus <- round(alpha_locus,2)
+
+self_eff_items <- satisfaction_data_usa[, c("selfeff_1", "selfeff_2", "selfeff_3")]
+alpha_self_eff <- alpha(self_eff_items)
+alpha_self_eff <- alpha_self_eff$total$raw_alpha
+alpha_self_eff <- round(alpha_self_eff,2)
+
+self_est_items <- satisfaction_data_usa[, c("selfest_1", "selfest_2", "selfest_3", "selfest_4", "selfest_5", "selfest_6", "selfest_7", "selfest_8", "selfest_9", "selfest_10")]
+alpha_self_est <- alpha(self_est_items, check.keys=TRUE)
+alpha_self_est <- alpha_self_est$total$raw_alpha
+alpha_self_est <- round(alpha_self_est,2)
+
+self_con_items <- satisfaction_data_usa[, c("selfcon_1", "selfcon_2", "selfcon_3", "selfcon_4", "selfcon_5", "selfcon_6", "selfcon_7", "selfcon_8", "selfcon_9", "selfcon_10", "selfcon_11", "selfcon_12", "selfcon_13")]
+alpha_self_con <- alpha(self_con_items, check.keys=TRUE)
+alpha_self_con <- alpha_self_con$total$raw_alpha
+alpha_self_con <- round(alpha_self_con,2)
+
+implicit_items <- satisfaction_data_usa[, c("lay_1", "lay_2", "lay_3", "lay_4", "lay_5r", "lay_6r", "lay_7r", "lay_8r")]
+alpha_implicit <- alpha(implicit_items, check.keys=TRUE)
+alpha_implicit <- alpha_implicit$total$raw_alpha
+alpha_implicit <- round(alpha_implicit,2)
+
 ## Construct Final Table
@@
   "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2,
-                                NA, NA, NA, NA, NA),
+                                alpha_locus, alpha_implicit, alpha_selfest, alpha_selfeff, alpha_self_con),
   Mean = c(

### 2024-02-14 scripts/02-data_cleaning.R

@@ -8,10 +8,14 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
 
-#### Clean data ####
+#### Clean WVS data ####
 wvs_data <- read_csv("inputs/data/study_3/WVS_TimeSeries_4_0.csv")
-wvs_data <- wvs_data %>% select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034)
+
+wvs_data_usa <- wvs_data %>% filter(COUNTRY_ALPHA == "USA") %>% 
+  dplyr::select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034, F198, G023, C031, X001, X003)
+wvs_data <- wvs_data %>% dplyr::select(COUNTRY_ALPHA, S020, S006, S007, A173, C033, C034)
 
 wvs_data <- wvs_data %>% rename(country_code = COUNTRY_ALPHA,
                                 year_survey = S020,
@@ -21,11 +25,57 @@ wvs_data <- wvs_data %>% rename(country_code = COUNTRY_ALPHA,
                                 jd = C034
                                 )
 
+wvs_data_usa <- wvs_data_usa %>% rename(country_code = COUNTRY_ALPHA,
+                                        Age = X003,
+                                        Sex = X001,
+                                         year_survey = S020,
+                                         unified_id = S007,
+                                         freewill = A173,
+                                         job_satisfaction = C033,
+                                         job_decision = C034,
+                                         job_pride = C031,
+                                         fate = F198,
+                                         autonomy = G023
+                                        )
+
+
 country_codes <- c("ARG", "BRA", "CHL", "CHN", "CZE", "IND", "JPN", "MEX", "NGA",
                    "POL", "RUS", "SVK", "ZAF", "KOR", "ESP", "CHE", "USA")
 
 wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>%
   filter(freewill > 0)
 
-#### Save data ####
+wvs_data_usa[wvs_data_usa < 0] <- NA
+
+#### Save WVS data ####
 write_csv(wvs_filtered, 'inputs/data/study_3/wvs_filtered.csv') # because original file is way too big
+write_csv(wvs_data_usa, 'outputs/data/wvs_data_usa.csv')
+
+## Clean Study 2 data ##
[…]

### 2024-02-14 scripts/06-replication-table2.R

@@ -97,6 +97,31 @@ alpha_jaut2 <- alpha(jaut2_items)
 alpha_jaut2 <- alpha_jaut2$total$raw_alpha
 alpha_jaut2 <- round(alpha_jaut2,2)
 
+locus_items <- satisfaction_data_usa[, c("lc1", "lc2", "lc3", "lc4", "lc5", "lc6", "lc7", "lc8", "lc9", "lc10", "lc11", "lc12", "lc13")]
+alpha_locus <- alpha(locus_items, check.keys=TRUE)
+alpha_locus <- alpha_locus$total$raw_alpha
+alpha_locus <- round(alpha_locus,2)
+
+self_eff_items <- satisfaction_data_usa[, c("selfeff_1", "selfeff_2", "selfeff_3")]
+alpha_self_eff <- alpha(self_eff_items)
+alpha_self_eff <- alpha_self_eff$total$raw_alpha
+alpha_self_eff <- round(alpha_self_eff,2)
+
+self_est_items <- satisfaction_data_usa[, c("selfest_1", "selfest_2", "selfest_3", "selfest_4", "selfest_5", "selfest_6", "selfest_7", "selfest_8", "selfest_9", "selfest_10")]
+alpha_self_est <- alpha(self_est_items, check.keys=TRUE)
+alpha_self_est <- alpha_self_est$total$raw_alpha
+alpha_self_est <- round(alpha_self_est,2)
+
+self_con_items <- satisfaction_data_usa[, c("selfcon_1", "selfcon_2", "selfcon_3", "selfcon_4", "selfcon_5", "selfcon_6", "selfcon_7", "selfcon_8", "selfcon_9", "selfcon_10", "selfcon_11", "selfcon_12", "selfcon_13")]
+alpha_self_con <- alpha(self_con_items, check.keys=TRUE)
+alpha_self_con <- alpha_self_con$total$raw_alpha
+alpha_self_con <- round(alpha_self_con,2)
+
+implicit_items <- satisfaction_data_usa[, c("lay_1", "lay_2", "lay_3", "lay_4", "lay_5r", "lay_6r", "lay_7r", "lay_8r")]
+alpha_implicit <- alpha(implicit_items, check.keys=TRUE)
+alpha_implicit <- alpha_implicit$total$raw_alpha
+alpha_implicit <- round(alpha_implicit,2)
+
 
 
 

### 2024-02-14 outputs/paper/paper.qmd
more edits

@@
 library(corrplot)
+library(countrycode)
 
 wvs_data_usa <- read_csv(here::here('outputs/data/wvs_data_usa.csv'))
+wvs_filtered <- read_csv("inputs/data/study_3/wvs_filtered.csv")
 satisfaction_data_usa <- read_csv(here::here('inputs/data/study_2/FW satisfaction-Study 2-data.csv'))
@@
 js1_items <- satisfaction_data_usa[, c("jobsat_1", "jobsat_2", "jobsat_3", "jobsat_4", "jobsat_5")]
-alpha_js1 <- alpha(js1_items)
+alpha_js1 <- alpha(js1_items, check.keys=TRUE)
 alpha_js1 <- alpha_js1$total$raw_alpha
@@
 js2_items <- satisfaction_data_usa[, c("jobsat2_1", "jobsat2_2", "jobsat2_3", "jobsat2_4", "jobsat2_5")]
-alpha_js2 <- alpha(js2_items)
+alpha_js2 <- alpha(js2_items, , check.keys=TRUE)
 alpha_js2 <- alpha_js2$total$raw_alpha
@@
 #| label: tbl-wvssummary
-#| tbl-cap: Summary Statistics for selected Psychological Constructs measured in the World Values Survey USA, 1981-2017
+#| tbl-cap: "Summary Statistics for selected Psychological Constructs measured in the World Values Survey USA, 1981-2017"
 
@@
   sd_pride= round(sd(job_pride, na.rm = TRUE),2),
-  mean_autonomy = round(mean(autonomy, na.rm = TRUE),2),
-  sd_autonomy = round(sd(autonomy, na.rm = TRUE),2))
+  )
 
@@
   Variable = c("Age","Belief in Free Will", "Job Satisfaction", 
-               "Job Autonomy", "Job Pride", "Fate vs. Control", "Personal Autonomy"),
+               "Job Autonomy", "Pride in Job", "Belief in Fate"),
   Mean = c(wvs_data_usa_summary$mean_age,
@@
            wvs_data_usa_summary$mean_pride,
-           wvs_data_usa_summary$mean_fate,
-           wvs_data_usa_summary$mean_autonomy),
+           wvs_data_usa_summary$mean_fate
+           ),
   SD = c(wvs_data_usa_summary$sd_age,
@@
          wvs_data_usa_summary$sd_pride,
-         wvs_data_usa_summary$sd_fate,
-         wvs_data_usa_summary$sd_autonomy))
+         wvs_data_usa_summary$sd_fate
+         ))
 
-wvs_data_usa_summary
+kable(wvs_data_usa_summary)
 
@@
 
-# Now, cor_matrix contains your full correlation matrix
 corrplot(cor_matrix, method = "circle", type='full', tl.col="black", sig.level = 0.05, insig = "blank")
@@
 ```
-In exploring free will beliefs and their impact on job satifaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends Feldman et al.'s results.
+In exploring free will beliefs and their impact on job satisfaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends Feldman et al.'s results.
 As seen in @fig-corst2, most variables are significantly correlated with each other, with the highest correlations being unsurprisingly between the two measurements of Job satisfaction.
@@
 ## National Sample (WVS)
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-corwvs
+#| fig-cap: "Correlation Matrix for selected Psychological Constructs measured in World Values Survey USA 1981-2017"
+#| fig-width: 10
+#| fig-height: 10
+
+wvs_data_usa_num <- wvs_data_usa %>% dplyr::select(freewill, job_satisfaction, job_decision, job_pride, fate)
+wvs_data_usa_num <- wvs_data_usa_num %>% rename("Belief in Free Will" = "freewill",
+                                                "Job Satisfaction" = "job_satisfaction",
+                                                "Job Autonomy" = "job_decision",
+                                                "Pride in Job" = "job_pride",
+                                                "Belief in Fate" = "fate",
+                                                )
+cor_matrix <- cor(wvs_data_usa_num, use = 'pairwise.complete.obs')
+
+corrplot(cor_matrix, method = "circle", type='full', tl.col="black", sig.level = 0.05, insig = "blank")
+
+cor_fw_js1 <- cor.test(wvs_data_usa_num$`Belief in Free Will`, 
+                   wvs_data_usa_num$`Job Satisfaction`, method = "pearson")
+
+cor_fw_js1_correlation_coefficient <- round(cor_fw_js1$estimate,2)
+cor_fw_js1_p_value <- cor_fw_js1$p.value
+cor_fw_js1_ci <- round(cor_fw_js1$conf.int,2)
+
+cor_js_jaut <- cor.test(wvs_data_usa_num$`Job Autonomy`, 
+                   wvs_data_usa_num$`Job Satisfaction`, method = "pearson")
+
+cor_js_jaut_correlation_coefficient <- round(cor_js_jaut$estimate,2)
+cor_js_jaut_p_value <- cor_js_jaut$p.value
+cor_js_jaut_ci <- round(cor_js_jaut$conf.int,2)
+
+cor_fw_jaut <- cor.test(wvs_data_usa_num$`Job Autonomy`, 
+                   wvs_data_usa_num$`Belief in Free Will`, method = "pearson")
+
+cor_fw_jaut_correlation_coefficient <- round(cor_fw_jaut$estimate,2)
+cor_fw_jaut_p_value <- cor_fw_jaut$p.value
+cor_fw_jaut_ci <- round(cor_fw_jaut$conf.int,2)
+
+cor_fw_fate <- cor.test(wvs_data_usa_num$`Belief in Fate`, 
+                   wvs_data_usa_num$`Belief in Free Will`, method = "pearson")
+
+cor_fw_fate_correlation_coefficient <- round(cor_fw_fate$estimate,2)
+cor_fw_fate_p_value <- cor_fw_fate$p.value
+cor_fw_fate_ci <- round(cor_fw_fate$conf.int,2)
+```
+As shown in @fig-corwvs, the results of the national-level World Values Survey also show a positive correlation between free will beliefs and job satisfaction (*r* = `r cor_fw_js1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`]).
+Similarly, job autonomy is highly correlated with job satisfaction (*r* = `r cor_js_jaut_correlation_coefficient`, *p* <.001, CI [`r cor_js_jaut_ci[1]`, `r cor_js_jaut_ci[2]`]) and with free will beliefs (*r* = `r cor_fw_jaut_correlation_coefficient`, *p* <.001, CI [`r cor_fw_jaut_ci[1]`, `r cor_fw_jaut_ci[2]`]).
+Since we created these psychological constructs based on single-item questions of the World Values Survey, internal validity and reliability cannot be guaranteed as concretely as with the Amazon Mechanical Turk survey sample.
+However, the construct 'Belief in Fate' negatively correlated with the belief in free will, as expected (*r* = `r cor_fw_fate_correlation_coefficient`, *p* <.001, CI [`r cor_fw_fate_ci[1]`, `r cor_fw_fate_ci[2]`]).
+Similarly, the construct 'Pride in Job' is positively correlated with all other variables except for the belief in fate, as expected.
+
+### Comparison to other countries
+```{r}
+wvs_summary_table <- wvs_filtered %>% group_by(country_code) %>% 
+  summarize("FW Mean"=round(mean(freewill),2), n=n())
+
+wvs_filtered_2 <- wvs_filtered %>% filter(js > 0)
+
+correlations <- wvs_filtered_2 %>%
+  group_by(country_code) %>%
+  do(correlation = cor(.$freewill, .$js, use = "complete.obs"))
+
+correlations <- wvs_filtered_2 %>%
+  group_by(country_code) %>%
+  summarize(correlation = list(cor(freewill, js, use = "complete.obs"))) %>%
+  ungroup() %>%
+  mutate(correlation = map_dbl(correlation, ~ round(.x, 2)))
+
+final_table <- left_join(wvs_summary_table, correlations, by = "country_code")
+final_table <- final_table %>% mutate("Country Name" = countrycode(country_code, "iso3c", "country.name"))
+final_table <- final_table[c(5, 2, 4, 3)]
+final_table <- final_table %>% rename("Correlation" = correlation)
+final_table
+```
 

### 2024-02-14 outputs/ssrp_report/ssrp_report.qmd
more edits

@@
 satisfaction_data_usa <- read_csv(here::here("inputs/data/study_2/FW satisfaction-Study 2-data.csv"))
-wvs_data <- read_csv(here::here("inputs/data/study_3/wvs_filtered.csv"))
+wvs_data <- read_csv(here::here("inputs/data/study_3/wvs_filtered_replication.csv"))
 

### 2024-02-14 scripts/02-data_cleaning.R

@@ -42,13 +42,20 @@ wvs_data_usa <- wvs_data_usa %>% rename(country_code = COUNTRY_ALPHA,
 country_codes <- c("ARG", "BRA", "CHL", "CHN", "CZE", "IND", "JPN", "MEX", "NGA",
                    "POL", "RUS", "SVK", "ZAF", "KOR", "ESP", "CHE", "USA")
 
-wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>%
+wvs_filtered_replication <- wvs_data %>% filter(country_code %in% country_codes) %>% filter(year_survey <= 2008) %>%
   filter(freewill > 0)
+
+wvs_filtered <- wvs_data %>% filter(country_code %in% country_codes) %>%
+  filter(freewill > 0)
+
 
 wvs_data_usa[wvs_data_usa < 0] <- NA
 
+wvs_data_usa <- wvs_data_usa %>% mutate(across(c("fate"), ~11 - .)) %>% mutate(across(c("job_pride"), ~4 - .))
+
 #### Save WVS data ####
-write_csv(wvs_filtered, 'inputs/data/study_3/wvs_filtered.csv') # because original file is way too big
+write_csv(wvs_filtered, 'outputs/data/wvs_filtered.csv')
+write_csv(wvs_filtered_replication, 'inputs/data/study_3/wvs_filtered.csv')
 write_csv(wvs_data_usa, 'outputs/data/wvs_data_usa.csv')
 
 ## Clean Study 2 data ##

### 2024-02-15 outputs/paper/paper.qmd
made edits to results section

@@
 library(countrycode)
+library(purrr)
 
 wvs_data_usa <- read_csv(here::here('outputs/data/wvs_data_usa.csv'))
-wvs_filtered <- read_csv("inputs/data/study_3/wvs_filtered.csv")
+wvs_filtered <- read_csv(here::here("inputs/data/study_3/wvs_filtered.csv"))
 satisfaction_data_usa <- read_csv(here::here('inputs/data/study_2/FW satisfaction-Study 2-data.csv'))
@@
 js2_items <- satisfaction_data_usa[, c("jobsat2_1", "jobsat2_2", "jobsat2_3", "jobsat2_4", "jobsat2_5")]
-alpha_js2 <- alpha(js2_items, , check.keys=TRUE)
+alpha_js2 <- alpha(js2_items, check.keys=TRUE)
 alpha_js2 <- alpha_js2$total$raw_alpha
@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-countries
+#| tbl-cap: Correlations Between Belief in Free Will and Job Satisfaction by Country in the World Values Survey
+
 wvs_summary_table <- wvs_filtered %>% group_by(country_code) %>% 
@@
   group_by(country_code) %>%
-  summarize(correlation = list(cor(freewill, js, use = "complete.obs"))) %>%
+  summarize(cor_stats = list(cor.test(freewill, js, use = "complete.obs")),
+            .groups = 'drop') %>%
   ungroup() %>%
-  mutate(correlation = map_dbl(correlation, ~ round(.x, 2)))
+  mutate(correlation = map_dbl(cor_stats, ~ round(.x$estimate, 2)),
+         p_value = map_dbl(cor_stats, ~ .x$p.value),
+         significance = case_when(
+           p_value <= 0.001 ~ "***",
+           p_value <= 0.01 ~ "**",
+           p_value <= 0.05 ~ "*",
+           TRUE ~ ""
+         ))
 
-final_table <- left_join(wvs_summary_table, correlations, by = "country_code")
-final_table <- final_table %>% mutate("Country Name" = countrycode(country_code, "iso3c", "country.name"))
-final_table <- final_table[c(5, 2, 4, 3)]
-final_table <- final_table %>% rename("Correlation" = correlation)
+final_table <- left_join(wvs_summary_table, correlations, by = "country_code") %>%
+  mutate(`Country Name` = countrycode(country_code, "iso3c", "country.name")) %>%
+  dplyr::select(`Country Name`, `FW Mean`, correlation, significance, n) %>%
+  rename(`Correlation` = correlation) %>%
+  mutate(Correlation = paste0(Correlation, significance)) %>% dplyr::select(-significance) %>% 
+  arrange(desc(`FW Mean`))
 final_table
+
+final_table %>%
+  kable("latex", booktabs = T) %>%
+  kable_styling(bootstrap_options = "striped") %>%
+  footnote(general ="FW Mean = National Average of the Belief in Free Will. \n n.s. p > .05. **p < .01. ***p < .001.") %>% 
+  row_spec(which(final_table$`Country Name` == "United States"), background = "#ADD8E6")
 ```
+
+In our analysis, we included data up until 2017 of the World Values Survey (2017), as opposed to only until 2008.
+This leads to slightly different results than in @feldman2017.
+Now, the correlations are statistically significant for all countries in the sample and we still observe that the belief in free will and job satisfaction varies similarly to the 2008 data.
+Compared to the 16 countries sampled in @feldman2017, the United States has a relatively high average belief in free will, coming second just after Mexico (@tbl-countries).
+While the correlation between the belief in free will and job satisfaction is not as high as in Mexico, it is still one of the stronger significant correlations in the sample of countries (*r* = 0.27, *p* <.001).
+
+### Demographic Factors
+
+```{r,include=FALSE,message=FALSE,warning=FALSE}
+anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
+summary(anova_result)
+```
+Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-appendix).
+ANOVA confirmed that there are no significant differences (*F*(4,12809) = 1.032, *p* = 0.358).
+
+\newpage
 
@@
 
-# Appendix {sec-appendix}
-## Step-Wise regression results {sec-apx-stepwise}
+# Appendix {#sec-appendix}
+## Step-Wise regression results {#sec-apx-stepwise}
 
@@
 
+## Demographic Boxplots for World Values Survey
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-ageboxplotwvs
+#| fig-cap: "Belief in Free Will by Age Group in WVS 1981-2022"
+
+wvs_data_usa$age_group <- cut(wvs_data_usa$Age,
+                    breaks = c(18, 30, 40, 50, 60, Inf),
+                    labels = c("18-30", "31-40", "41-50", "51-60", "Over 60"),
+                    right = FALSE)
+
+wvs_data_usa %>% drop_na(age_group) %>% ggplot(aes(x = age_group, y = freewill)) +
+  geom_boxplot(fill = "lightblue") +
+  labs(
+       x = "Age Group",
+       y = "Belief in Free Will") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  + theme_minimal()
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-sexboxplotwvs
+#| fig-cap: "Belief in Free Will by Age Group in WVS 1981-2022"
+
+wvs_data_usa %>% drop_na(Sex) %>% ggplot(aes(x = factor(Sex, labels = c("Male", "Female")), y = freewill)) +
+  geom_boxplot(fill = "lightblue") +
+  labs(
+       x = "Sex",
+       y = "Belief in Free Will") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  + theme_minimal()
+
+```
+
 \newpage

### 2024-02-15 scripts/03-test_data.R
test data

@@ -1,15 +1,54 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the cleaned free will paper dataset
+# Author: Sami El Sabri & Liban Timir
+# Date: 15 February 2024
+# Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
 # [...UPDATE THIS...]
 
+#### Read in data ####
+wvs_data_usa <- read_csv(here::here('outputs/data/wvs_data_usa.csv'))
+
 #### Test data ####
+test_that("Free Will scale scores are within the 1-6 range", {
+  expect_true(all(wvs_data_usa$freewill >= 1 & wvs_data_usa$freewill <= 6), 
+              info = "There are scores outside the 1-6 range in the Free Will 
+              scale")
+})
+
+test_that("Job Satisfaction scale values are within the 1-7 range", {
+  expect_true(all(wvs_data_usa$job_satisfaction >= 1 & 
+                    wvs_data_usa$job_satisfaction <= 7),
+              info = "Job Satisfaction scale values are out of the 1-7 range")
+})
+
+test_that("Data types are correct", {
+  expect_is(wvs_data_usa$freewill, "numeric", 
+            info = "Free Will scale is not numeric")
+  expect_is(wvs_data_usa$job_satisfaction, "numeric",
+            info = "Job Satisfaction is not numeric")
+})
+
+test_that("Dataset has the expected number of rows", {
+  expected_number_of_rows <- 12983  
+  actual_number_of_rows <- nrow(wvs_data_usa)
+  expect_equal(actual_number_of_rows, expected_number_of_rows,
+               info = "The dataset does not have the expected number of rows.")
+})
+
+test_that("Values in specified columns are positive", {
+  columns_to_check <- c("freewill", "job_satisfaction")
+  for (column_name in columns_to_check) {
+    expect_true(all(your_dataframe[[column_name]] > 0),
[…]

### 2024-02-15 scripts/00-simulate_data.R
final simulate, download, cleaning, and test scripts

@@ -1,19 +1,46 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates the Feldman et al. (2017) and WVS data
+# Author: Sami El Sabri, Liban Timir
+# Date: 15 February 2024
+# Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(dplyr)
+library(lubridate)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(555) 
 
+num_rows <- 100  
 
+ids <- 1:num_rows
 
+# Simulating free will and job satisfaction scores at two time points
+# Assuming free will is measured on a scale from 1 to 6, 
+# job satisfaction from 1 to 7
+free_will_T1 <- runif(num_rows, min = 1, max = 6)
+free_will_T2 <- runif(num_rows, min = 1, max = 6)
+job_satisfaction_T1 <- runif(num_rows, min = 1, max = 7)
+job_satisfaction_T2 <- runif(num_rows, min = 1, max = 7)
+
+# Simulating job autonomy scores at two time points, 
+# also on a scale from 1 to 7
+job_autonomy_T1 <- runif(num_rows, min = 1, max = 7)
+job_autonomy_T2 <- runif(num_rows, min = 1, max = 7)
+
+# Creating a data frame with the simulated data
+simulated_data <- data.frame(
+  ID = ids,
+  Free_Will_T1 = free_will_T1,
+  Free_Will_T2 = free_will_T2,
+  Job_Satisfaction_T1 = job_satisfaction_T1,
+  Job_Satisfaction_T2 = job_satisfaction_T2,
+  Job_Autonomy_T1 = job_autonomy_T1,
+  Job_Autonomy_T2 = job_autonomy_T2
+)
+
+# Viewing the first few rows of the simulated dataset
+head(simulated_data)

### 2024-02-15 scripts/01-download_data.R

@@ -2,7 +2,7 @@
 # Purpose: Downloads and saves the data necessary
 # Authors: Sami El Sabri, Liban Timir
 # Date: 10 February 2023
-# Contact: sami.elsabri@mail.utoronto.ca
+# Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Download 1.3GB large file titled 'WVS TimeSeries 1981 2022 Csv v4 0.zip' from 
 # https://www.worldvaluessurvey.org/WVSDocumentationWVL.jsp

### 2024-02-15 scripts/02-data_cleaning.R

@@ -2,7 +2,7 @@
 # Purpose: Cleans the raw data provided by Feldman et al. (2017) and by WVS
 # Authors: Sami El Sabri, Liban Timir
 # Date: 10 February 2023
-# Contact: sami.elsabri@mail.utoronto.ca
+# Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 01-download_data.R
 

### 2024-02-15 scripts/03-test_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Tests the cleaned free will paper dataset
+# Purpose: Tests the cleaned data provided by Feldman et al. (2017) and by WVS
 # Author: Sami El Sabri & Liban Timir
 # Date: 15 February 2024
 # Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca

### 2024-02-15 scripts/03-test_data.R
slight edit to test data

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Tests the cleaned data provided by Feldman et al. (2017) and by WVS
-# Author: Sami El Sabri & Liban Timir
+# Author: Sami El Sabri, Liban Timir
 # Date: 15 February 2024
 # Contact: sami.elsabri@mail.utoronto.ca, liban.timir@mail.utoronto.ca
 # License: MIT

### 2024-02-15 outputs/paper/paper.qmd
added comparative section to results

@@
 ```{r,include=FALSE,message=FALSE,warning=FALSE}
+# inferential statistics age group and freewill
 anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
 summary(anova_result)
+model <- lm(job_satisfaction~ freewill * age_group, data = wvs_data_usa)
+summary(model)
+
+# inferential statistics sex and freewill
+t.test(freewill ~ Sex, data = wvs_data_usa )
+
+lm_interaction <- lm(job_satisfaction ~ freewill * factor(Sex), data = wvs_data_usa)
+summary(lm_interaction)
 ```
-Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-appendix).
+Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-apx-box).
 ANOVA confirmed that there are no significant differences (*F*(4,12809) = 1.032, *p* = 0.358).
+Age did also not influence the relationship between free will beliefs and job satisfaction (lowest *p* = 0.293).
+However, there is a significant difference of Sex on free will beliefs (@fig-sexboxplotwvs in @sec-apx-box), with women on average having marginally higher ratings (7.69) than men (7.61) (*p* < 0.05).
+We could not observe any significant effect of Sex on the relationship between free will beliefs and job satisfaction (*p* = 0.40).
+
+## Comparison to Amazon Mechanical Turk Sample
+```{r}
+# Normalize free will scores between the two samples
+satisfaction_data_usa_rel_num$freewill_norm <- (satisfaction_data_usa_rel_num$`Belief in Free Will (T1)` - 1)/(6-1)
+
+wvs_data_usa$freewill_norm <- (wvs_data_usa$freewill - 1)/(10-1)
+
+freewill_norm_mean_turk <- mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE)
+
+freewill_norm_mean_wvs <- mean(wvs_data_usa$freewill_norm, na.rm = TRUE)
+
+```
 
@@
 
-## Demographic Boxplots for World Values Survey
+## Demographic Boxplots for World Values Survey {#sec-apx-box}
 ```{r}

### 2024-02-15 outputs/paper/paper.qmd
finished results section

@@
 
+\newpage
 ## National Sample (WVS)
@@
   arrange(desc(`FW Mean`))
-final_table
 
@@
   kable_styling(bootstrap_options = "striped") %>%
-  footnote(general ="FW Mean = National Average of the Belief in Free Will. \n n.s. p > .05. **p < .01. ***p < .001.") %>% 
+  footnote(general ="FW Mean = National Average of the Belief in Free Will",
+            symbol = "n.s. p > .05. **p < .01. ***p < .001.") %>% 
   row_spec(which(final_table$`Country Name` == "United States"), background = "#ADD8E6")
@@
 ```{r,include=FALSE,message=FALSE,warning=FALSE}
+
+wvs_data_usa$age_group <- cut(wvs_data_usa$Age,
+                    breaks = c(18, 30, 40, 50, 60, Inf),
+                    labels = c("18-30", "31-40", "41-50", "51-60", "Over 60"),
+                    right = FALSE)
+
 # inferential statistics age group and freewill
-anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
+anova_result <- aov(freewill ~ age_group, data =wvs_data_usa)
 summary(anova_result)
@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-comparison
+#| tbl-cap: Comparative Summary Statistics Between Amazon MTurk and WVS Samples
+
 # Normalize free will scores between the two samples
 satisfaction_data_usa_rel_num$freewill_norm <- (satisfaction_data_usa_rel_num$`Belief in Free Will (T1)` - 1)/(6-1)
+satisfaction_data_usa_rel_num$jobsatisfaction_norm <- (satisfaction_data_usa_rel_num$`Job Satisfaction (T1)` - 1)/(7-1)
 
 wvs_data_usa$freewill_norm <- (wvs_data_usa$freewill - 1)/(10-1)
+wvs_data_usa$jobsatisfaction_norm <- (wvs_data_usa$job_satisfaction - 1)/(10-1)
 
-freewill_norm_mean_turk <- mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE)
+# Calculate means and sd of those normalized scores
 
-freewill_norm_mean_wvs <- mean(wvs_data_usa$freewill_norm, na.rm = TRUE)
+freewill_norm_mean_turk <- round(mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE),2)
+freewill_norm_sd_turk <- round(sd(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE),2)
+jobsat_norm_mean_turk <- round(mean(satisfaction_data_usa_rel_num$jobsatisfaction_norm, na.rm = TRUE),2)
+jobsat_norm_sd_turk <- round(sd(satisfaction_data_usa_rel_num$jobsatisfaction_norm, na.rm = TRUE),2)
+
+freewill_norm_mean_wvs <- round(mean(wvs_data_usa$freewill_norm, na.rm = TRUE),2)
+freewill_norm_sd_wvs <- round(sd(wvs_data_usa$freewill_norm, na.rm = TRUE),2)
+jobsat_norm_mean_wvs <- round(mean(wvs_data_usa$jobsatisfaction_norm, na.rm = TRUE),2)
+jobsat_norm_sd_wvs <- round(sd(wvs_data_usa$jobsatisfaction_norm, na.rm = TRUE),2)
+
+comparative_summary_table <- data.frame(
+  "Variable" = c("Belief in Free Will", "Job Satisfaction"),
+  "Mean" = c(freewill_norm_mean_turk, jobsat_norm_mean_turk),
+  "SD" = c(freewill_norm_sd_turk, jobsat_norm_sd_turk),
+  "Mean" = c(freewill_norm_mean_wvs, jobsat_norm_mean_wvs),
+  "SD" = c(freewill_norm_sd_wvs,jobsat_norm_sd_wvs),
+  check.names = FALSE)
+
+comparative_summary_table %>%
+  kable("latex", booktabs = T) %>%
+  kable_styling(bootstrap_options = "striped") %>% add_header_above(c(" " = 1, "MTurk Sample" = 2, "WVS Sample" = 2))
+
+t_test_result_fw <- t.test(satisfaction_data_usa_rel_num$freewill_norm, wvs_data_usa$freewill_norm)
+
+t_test_result_js <- t.test(satisfaction_data_usa_rel_num$jobsatisfaction_norm, wvs_data_usa$jobsatisfaction_norm)
 
 ```
+
+Since the two samples use different scales to measure belief in free will and job satisfaction, we normalized the values (mapping it onto a scale from 0 to 1), such that we can compare them directly (@tbl-comparison).
+Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* < 0.001, CI [`r t_test_result_fw$conf.int[1]`, `r t_test_result_fw$conf.int[2]`]).
+The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* < 0.001, CI [`r t_test_result_js$conf.int[1]`, `r t_test_result_js$conf.int[2]`]).
 
@@
 
-wvs_data_usa$age_group <- cut(wvs_data_usa$Age,
-                    breaks = c(18, 30, 40, 50, 60, Inf),
-                    labels = c("18-30", "31-40", "41-50", "51-60", "Over 60"),
-                    right = FALSE)
-
 wvs_data_usa %>% drop_na(age_group) %>% ggplot(aes(x = age_group, y = freewill)) +

### 2024-02-15 outputs/paper/paper.qmd
added sketches and some citations

@@
 subtitle: "Nowhere near done yet! We had significant issues with our last dataset and had to restart, so bare with us."
-author: 
-  - Sami El Sabri
-  - Liban Timir
+author: Sami El Sabri and Liban Timir
 thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis.
@@
 
-Utilizing the same dataset and a similar methodology to Feldman et al.
-(2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality.
+Utilizing the same dataset and a similar methodology to @feldman2017, we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality.
 While Feldman et al.
@@
 The estimand is the correlation between the belief in free will and job satisfaction.
-Our reproduction was conducted using the statistical programming language R (@citeR).
-In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc).
+Our reproduction was conducted using the statistical programming language R [@citeR].
+In the data analysis and visualization process, we also made use of the following R packages: tidyverse [@citetidyverse], dplyr [@citedplyr], knitr [@citeknitr], kableExtra [@citekExtra], purrr [@citepurrr], psych [@citepsych], car [@citecar], MASS [@citeMASS], and countrycode [@citecc].
 
@@
 This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.
-### TALK ABOUT FINDINGS HERE###
+\### TALK ABOUT FINDINGS HERE###
 
 # Data {#sec-data}
+
 ## Source {#sec-source}
-Dataset Overview:
 
-Introduction to the Dataset: Start by providing a brief overview of the dataset(s) used, including the source (e.g., Amazon Mechanical Turk, World Values Survey) and the rationale for selecting these datasets for replication.
-Scope and Scale: Mention the size of the dataset, the number of participants, and the time frame covered by the data collection.
+For the purposes of this paper, we make use of two distinct data sources.
+
+The first data source is original survey data conducted by @feldman2017 on Amazon Mechanical Turk (MTurk), a popular online platform connecting "requesters" who offer tasks with "workers" who complete them for payment.
+The platform hosts a diverse, global workforce engaging in a range of tasks, from simple questionnaires to complex assignments requiring specialized skills.
+Compensation varies widely, with the average task priced at several dollars for about half an hour's work.
+This study surveyed American MTurk workers across two waves about their job satisfaction on MTurk, reflecting their overall work experience on the platform.
+The initial survey included 209 participants, with a follow-up six months later achieving a 66% response rate.
+@feldman2017 only included American workers in their study, making this data source appropriate for this investigation.
+The raw dataset comprised 143 variables, including both demographic variables and survey items relating to the outcomes and controls of interest.
+
+The second data source is the World Values Survey (@citewvs), which is a large cross-cultural and cross-occupational survey collected in waves between 1981 and 2022 of 450,869 participants from over 40 countries.
+@feldman2017 used the WVS of 2008 and included a sample of 16 countries.
+In our own analysis, we used the most recent dataset and filtered for the same sample of 16 countries, as well as for data on the United States of America.
+These filtered datasets comprised 136,171 and 12,983 participants, respectively and only included a small subset of nine the survey questions (including demographic information).
+
 ## Measurement {#sec-measurement}
-Variables Description:
 
-Dependent Variable(s): Describe the main variable of interest, job satisfaction, including how it was measured or operationalized in the dataset.
-Independent Variable(s): Explain the measurement of free will beliefs and any other relevant variables that were analyzed as predictors or controls in the study (e.g. job autonomy, self-efficacy etc.)
+### Belief in Free Will
 
-Covariates and Controls: If applicable, detail any additional variables used as controls or covariates in your analysis, such as demographic information, employment characteristics, or cultural factors.
+@feldman2017 measured belief in free will based on an adapted 9-item personal agency and free will subscale of the "Free Will and Determinism Scale" [@rakos2008].
+Participants indicated their responses from 1 (Strongly disagree) to 6 (Strongly Agree) on the following nine items:
 
-GO INTO GREAT DETAIL WITH MEASUREMENT!
+1.  I have free will
+2.  Free will is a part of the human spirit
+3.  Free will is a basic part of human nature
+4.  I have free will even when my choices are limited by external circumstances
+5.  People have free will regardless of wealth or life circumstances
+6.  Life's experiences cannot eliminate a person's free will
+7.  I am in charge of the decisions I make
+8.  I decide what action to take in a particular situation
+9.  I am in charge of my actions even when my life's circumstances are difficult
 
-In order to assess the internal validity and reliability of the psychological constructs measured in @feldman2017, we verified the Cronbach-Alpha reliability coefficients based on the raw dataset.
+As seen in @tbl-reliability, the reliability coefficient for this subscale indeed measuring the belief in free will is $\alpha$ = 0.88.
+The full scale by @rakos2008 additionally includes psychological constructs related to moral and personal responsibility, higher power control etc., but these were deemed as weakening the reliability of this measure [@feldman2017].
+
+In the WVS, we followed the assumption [@clark2014, @feldman2017] that the following item (A173 in the raw survey dataset) accurately assesses belief in free will: "“Indicate how much freedom of choice and control you feel you have over the way your life turns out” *(1 = no choice and control to 10 = a great deal of choice and control)*.
+This WVS item was previously used as a measure of the belief in free will [@clark2014]
+
+### Job Satisfaction
+In @feldman2017, job satisfaction was measured using a 5-item short scale version of @brayfield1951, constructed by @judge1998.
+Participants indicated their responses from 1 (Strongly disagree) to 7 (Strongly Agree) on the following five items:
+
+1. I feel fairly well satisfied with my present job doing MTurk tasks
+2. Most days I am enthusiastic about the work I do on MTurk
+3. Every time I work on tasks on MTurk it feels like forever (reversed)
+4. I find real enjoyment in the work I do on MTurk
+5. I consider the kind of work I do on MTurk rather unpleasant (reversed)
+
+Items 3 and 5 were inverted as a data cleaning step in order to correctly calculate correlations.
+Job Satisfaction was measured at two time points (three months apart) by @feldman2017, but at both times the reliability coefficients were fairly high ($\alpha$ = 0.79 and $\alpha$ = 0.84), indicating that these five items indeed measure job satisfaction among MTurk workers in the sample.
+
+In the WVS, we followed @feldman2017 and @dobrow2016 and used the following item (C033): “Overall, how satisfied or dissatisfied are you with your job?” *(1 = dissatisfied to 10 = satisfied)*.
+
+### Job Autonomy
+Job Autonomy was measured using a 3-item scale by @hackman1980, which @feldman2017 adapted for MTurk.
+Participants indicated their responses from (Strongly disagree) to 7 (Strongly Agree) on the following three items:
+
+1. I have significant autonomy in determining how I do my job on MTurk
+2. I can decide on my own how to go about doing my work on MTurk
+3. I have considerable opportunity for independence and freedom in how I do my job on MTurk
+
+@feldman2017 measured job autonomy also at two time points, with comparably high reliability coefficients ($\alpha$ = 0.83 and $\alpha$ = 0.85), also supporting the assumption that the above scale measures job autonomy accurately.
+
+In the WVS, we directly replicated @feldman2017 and used the following single-item survey question (C034): “How free are you to make decisions in your job?” *(1 = none at all to 10 = a great deal)*.
+
+### Control Variables
+In the MTurk dataset, we included all of @feldman2017 control variables (locus of control, self-control, self-esteem, self-efficacy, and implicit beliefs), which are all measured with similarly phrased survey questions as the aforementioned variables of interest.
+See the appendix (@sec-apx-controls) for detailed survey questions.
 As shown in @tbl-reliability, we were able to successfully replicate the coefficients for most constructs.
-The only deviation is with the trait locus of control, which has a coefficient α = .58 in @rotter1966, but 0.61 in our replication, indicating even greater confidence that the survey questions indeed measure the underlying construct.
+The only deviation is with the trait locus of control, which has a coefficient $\alpha$ = 0.58 in @rotter1966, but 0.61 in our replication, indicating even greater confidence that the survey questions indeed measure the underlying construct.
+
+For their analysis of the WVS data, @feldman2017 did not include any control variables.
+Since we were interested in understanding more about the relationships between the variables at the national level, we included the following two variables:
+
+* Belief in Fate: We expect this variable to negatively correlate with belief in free will, such that it can serve as some indication of internal validity and reliability.
+Not all waves of WVS data asked this question, but where possible we used the following question (F198):
+  + Some people believe that individuals can decide their own destiny, while others think that it is impossible to escape a predetermined fate.
+Please tell me which comes closest to your view on this scale on which 1 means “everything in life is determined by fate,” and 10 means that “people shape their fate themselves.”
+  + We inverted this scale, such that 1 means "people shape their fate themselves.” and 10 means “everything in life is determined by fate”, making it more consistent with the ordering logic of other variables used.
+
+* Pride in Job: We expect this variable to positively correlate with job satisfaction and job autonomy, such that it can serve as some indication of internal validity and reliability.
+Not all waves of WVS data asked this question, but where possible we used the following question (C031):
+  + How much pride, if any, do you take in the work that you do? (1 = "A great deal", 3 = "Little").
+  + We also inverted this scale, such that 1 means "Little" and 3 means "A great deal", making it making it more consistent with the ordering logic of other variables used.
 
@@
 #| label: tbl-reliability
-#| tbl-cap: Cronbach Alpha Reliability Coefficients for Psychological Constructs measured in Feldman et al. (2017)
+#| tbl-cap: Cronbach Alpha Reliability Coefficients for Psychological Constructs measured in Feldman et al. (2018)
 
@@
 ```
+\newpage
+## Data Characteristics {#sec-characteristics}
 
-## Data Characteristics {#sec-characteristics}
 The original research survey data published by @feldman2017 did not require any further data cleaning.
@@
 #| label: tbl-st2summary
-#| tbl-cap: Summary Statistics for Psychological Constructs measured in Feldman et al. (2017)
+#| tbl-cap: Summary Statistics for Psychological Constructs measured in Feldman et al. (2018)
 
@@
 
-Summary Statistics and Initial Observations:
+# Results {#sec-results}
 
-Descriptive Statistics: Provide summary statistics for the main variables, including means, standard deviations, and ranges.
-This gives readers a sense of the data's central tendencies and variability.
-Visualizations: Include graphs or tables that offer an initial view of the data, such as distributions of job satisfaction and free will beliefs.
-Discuss any notable patterns or preliminary observations.
-Comparative Analysis (if applicable):
+## Amazon Mechanical Turk Sample
 
-Comparison with Original Study: If you have access to summary statistics or data visualizations from the Feldman et al.
-study, briefly compare those findings with your dataset to highlight similarities or differences.
-Rationale for Differences: Discuss any expected or surprising differences in the data between the original study and your replication effort, potentially attributable to cultural or temporal differences.
-
-# Results {#sec-results}
-## Amazon Mechanical Turk Sample
 ```{r}
@@
 #| label: fig-corst2
-#| fig-cap: Correlation Matrix for Psychological Constructs measured in Study 2 of Feldman et al. (2017)
+#| fig-cap: Correlation Matrix for Psychological Constructs measured in Study 2 of Feldman et al. (2018)
 #| fig-width: 10
@@
 ```
+
 In exploring free will beliefs and their impact on job satisfaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends Feldman et al.'s results.
@@
 Locus of control lacks any significant correlations, which together with its low reliability coefficient designates it as a less decisive control variable.
-The most important relationship, however, is between free will beliefs and job satisfaction: The belief in free will was significantly positively correlated with job satisfaction both at Time 1 (*r* = `r cor_fw_js1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`]) and at Time 2 ( (r = `r cor_fw_js2_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js2_ci[1]`, `r cor_fw_js1_ci[2]`])).
-However, this correlation is not as strong as the one between free will beliefs and job autonomy (*r* = `r cor_fw_jaut1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_jaut1_ci[1]`, `r cor_fw_jaut1_ci[2]`]).
+The most important relationship, however, is between free will beliefs and job satisfaction: The belief in free will was significantly positively correlated with job satisfaction both at Time 1 (*r* = `r cor_fw_js1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`\]) and at Time 2 ( (r = `r cor_fw_js2_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js2_ci[1]`, `r cor_fw_js1_ci[2]`\])).
+However, this correlation is not as strong as the one between free will beliefs and job autonomy (*r* = `r cor_fw_jaut1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_jaut1_ci[1]`, `r cor_fw_jaut1_ci[2]`\]).
 This supports the claim that job autonomy may be the most important mediating variable between free will beliefs and job satisfaction.
-Moreover, a step-wise multiple regression on job satisfaction with all psychological agency constructs (full results in @sec-apx-stepwise) confirmed that the effect of free will beliefs on job satisfaction is robust and the strongest relative impact, even when controlling for other agency constructs (Time 1: *p* < 0.034; Time 2: *p* < 0.031).
+Moreover, a step-wise multiple regression on job satisfaction with all psychological agency constructs (full results in @sec-apx-stepwise) confirmed that the effect of free will beliefs on job satisfaction is robust and the strongest relative impact, even when controlling for other agency constructs (Time 1: *p* \< 0.034; Time 2: *p* \< 0.031).
 
@@
 ### Demographic Factors
+
 @fig-ageboxplotst2 shows that there are slight differences in the median belief in free will among the age groups.
@@
 
-Looking at sex (@fig-sexboxplotst2), on the other hand, we observe a significant difference in the belief in free will, with women having on average higher ratings of believing in free will (*p* < 0.05).
+Looking at sex (@fig-sexboxplotst2), on the other hand, we observe a significant difference in the belief in free will, with women having on average higher ratings of believing in free will (*p* \< 0.05).
 However, the effect of sex on the relationship between free will beliefs and job satisfaction has not been found to be significant (*p* = 0.58).
@@
 \newpage
+
 ## National Sample (WVS)
+
 ```{r}
@@
 ```
-As shown in @fig-corwvs, the results of the national-level World Values Survey also show a positive correlation between free will beliefs and job satisfaction (*r* = `r cor_fw_js1_correlation_coefficient`, *p* <.001, CI [`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`]).
-Similarly, job autonomy is highly correlated with job satisfaction (*r* = `r cor_js_jaut_correlation_coefficient`, *p* <.001, CI [`r cor_js_jaut_ci[1]`, `r cor_js_jaut_ci[2]`]) and with free will beliefs (*r* = `r cor_fw_jaut_correlation_coefficient`, *p* <.001, CI [`r cor_fw_jaut_ci[1]`, `r cor_fw_jaut_ci[2]`]).
+
+As shown in @fig-corwvs, the results of the national-level World Values Survey also show a positive correlation between free will beliefs and job satisfaction (*r* = `r cor_fw_js1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`\]).
+Similarly, job autonomy is highly correlated with job satisfaction (*r* = `r cor_js_jaut_correlation_coefficient`, *p* \<.001, CI \[`r cor_js_jaut_ci[1]`, `r cor_js_jaut_ci[2]`\]) and with free will beliefs (*r* = `r cor_fw_jaut_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_jaut_ci[1]`, `r cor_fw_jaut_ci[2]`\]).
 Since we created these psychological constructs based on single-item questions of the World Values Survey, internal validity and reliability cannot be guaranteed as concretely as with the Amazon Mechanical Turk survey sample.
-However, the construct 'Belief in Fate' negatively correlated with the belief in free will, as expected (*r* = `r cor_fw_fate_correlation_coefficient`, *p* <.001, CI [`r cor_fw_fate_ci[1]`, `r cor_fw_fate_ci[2]`]).
+However, the construct 'Belief in Fate' negatively correlated with the belief in free will, as expected (*r* = `r cor_fw_fate_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_fate_ci[1]`, `r cor_fw_fate_ci[2]`\]).
 Similarly, the construct 'Pride in Job' is positively correlated with all other variables except for the belief in fate, as expected.
@@
 ### Comparison to other countries
+
 ```{r}
@@
 Compared to the 16 countries sampled in @feldman2017, the United States has a relatively high average belief in free will, coming second just after Mexico (@tbl-countries).
-While the correlation between the belief in free will and job satisfaction is not as high as in Mexico, it is still one of the stronger significant correlations in the sample of countries (*r* = 0.27, *p* <.001).
+While the correlation between the belief in free will and job satisfaction is not as high as in Mexico, it is still one of the stronger significant correlations in the sample of countries (*r* = 0.27, *p* \<.001).
 
@@
 ```
+
 Interestingly, there are virtually no differences in the average belief in free will between the different age groups surveyed (@fig-ageboxplotwvs in @sec-apx-box).
@@
 Age did also not influence the relationship between free will beliefs and job satisfaction (lowest *p* = 0.293).
-However, there is a significant difference of Sex on free will beliefs (@fig-sexboxplotwvs in @sec-apx-box), with women on average having marginally higher ratings (7.69) than men (7.61) (*p* < 0.05).
+However, there is a significant difference of Sex on free will beliefs (@fig-sexboxplotwvs in @sec-apx-box), with women on average having marginally higher ratings (7.69) than men (7.61) (*p* \< 0.05).
 We could not observe any significant effect of Sex on the relationship between free will beliefs and job satisfaction (*p* = 0.40).
@@
 ## Comparison to Amazon Mechanical Turk Sample
+
 ```{r}
@@
 Since the two samples use different scales to measure belief in free will and job satisfaction, we normalized the values (mapping it onto a scale from 0 to 1), such that we can compare them directly (@tbl-comparison).
-Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* < 0.001, CI [`r t_test_result_fw$conf.int[1]`, `r t_test_result_fw$conf.int[2]`]).
-The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* < 0.001, CI [`r t_test_result_js$conf.int[1]`, `r t_test_result_js$conf.int[2]`]).
+Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* \< 0.001, CI \[`r t_test_result_fw$conf.int[1]`, `r t_test_result_fw$conf.int[2]`\]).
+The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* \< 0.001, CI \[`r t_test_result_js$conf.int[1]`, `r t_test_result_js$conf.int[2]`\]).
 
@@
 # Appendix {#sec-appendix}
+
+## Control Variables Survey Items {#sec-apx-controls}
+**Self-Control Scale**
+1. I am good at resisting temptation.
+2. I have a hard time breaking bad habits. (R)
+3. I am lazy. (R)
+4. I say inappropriate things. (R)
+5. I do certain things that are bad for me, if they are fun. (R)
+6. I refuse things that are bad for me.
+7. I wish I had more self-discipline. (R)
+8. People would say that I have iron self- discipline.
+9. Pleasure and fun sometimes keep me from getting work done. (R)
+10. I have trouble concentrating.(R)
+11. I am able to work effectively toward long-term goals.
+12. Sometimes I can’t stop myself from doing something, even if I know it is wrong. (R)
+13. I often act without thinking through all the alternatives. (R)
+
+Scale: 1 – Not at all; 5 – Very much.
+
+**Locus of Control**
+1.
+a. Children get into trouble because their patents punish them too much.
+b. The trouble with most children nowadays is that their parents are too easy with
+them.
+7
+2.
+a. Many of the unhappy things in people's lives are partly due to bad luck.
+b. People's misfortunes result from the mistakes they make.
+3.
+a. One of the major reasons why we have wars is because people don't take enough
+interest in politics.
+b. There will always be wars, no matter how hard people try to prevent them.
+4.
+a. In the long run people get the respect they deserve in this world.
+b. Unfortunately, an individual's worth often passes unrecognized no matter how hard
+he tries.
+5.
+a. The idea that teachers are unfair to students is nonsense.
+b. Most students don't realize the extent to which their grades are influenced by
+accidental happenings.
+6.
+a. Without the right breaks, one cannot be an effective leader.
+b. Capable people who fail to become leaders have not taken advantage of their
+opportunities.
+7.
+a. No matter how hard you try, some people just don't like you.
+b. People who can't get others to like them don't understand how to get along with
+others.
+8.
+a. Heredity plays the major role in determining one's personality.
+b. It is one's experiences in life which determine what they're like.
+9.
+a. I have often found that what is going to happen will happen.
+b. Trusting fate has never turned out as well for me as making a decision to take a
+definite course of action.
+10.
+a. In the case of the well prepared student there is rarely, if ever, such a thing as an
+unfair test.
+b. Many times, exam questions tend to be so unrelated to course work that studying is
+really useless.
+11.
+a. Becoming a success is a matter of hard work, luck has little or nothing to do with it.
+b. Getting a good job depends mainly on being in the right place at the right time.
+12.
+a. The average citizen can have an influence in government decisions.
+b. This world is run by the few people in power, and there is not much the little guy can
+do about it.
+13.
+a. When I make plans, I am almost certain that I can make them work.
+b. It is not always wise to plan too far ahead because many things turn out to be a
+matter of good or bad fortune anyhow.
+
+Score one point for response ‘a’ to questions: 1, 3, 4, 5, 10, 11, 12, and 13.
+
+Score one point for response ‘b’ to questions: 2, 6, 7, 8, and 9.
+
+**Self-esteem**
+1. I feel that I am a person of worth, at least on an equal basis with others.
+2. I feel that I have a number of good qualities.
+3. All in all, I am inclined to feel that I am a failure. (R)
+4. I am able to do things as well as most other people.
+5. I feel that I do not have much to be proud of. (R)
+6. I take a positive attitude toward myself.
+7. On the whole, I am satisfied with myself.
+8. I wish I could have more respect for myself. (R)
+9. I certainly feel useless at times. (R)
+10. At times I think I am no good at all. (R)
+Scale: 1 – Strongly disagree; 7 – Strongly agree.
+
+**Self-efficacy**
+1. I am strong enough to overcome life's struggles.
+2. At root, I am a weak person. (R)
+3. I can handle the situations that life brings.
+4. I usually feel that I am an unsuccessful person. (R)
+5. I often feel that there is nothing that I can do well. (R)
+6. I feel competent to deal effectively with the real world.
+7. I often feel like a failure. (R)
+8. I usually feel I can handle the typical problems that come up in life.
+Scale: 1 – Strongly disagree; 7 – Strongly agree.
+
+**Implicit beliefs**
+1. The kind of person someone is, is something very basic about them, and it can't be changed
+very much.
+2. People can do things differently, but the important parts of who they are can't really be
+changed.
+3. Everyone is a certain kind of person, and there is not much that they can do to really change
+that.
+4. As much as I hate to admit it, you can't teach an old dog new tricks. People can't really
+change their deepest attributes.
+5. Everyone, no matter who they are, can significantly change their basic characteristics. (R)
+6. People can substantially change the kind of person they are. (R)
+7. No matter what kind of person someone is, they can always change very much. (R)
+8. People can change even their most basic qualities. (R)
+Scale: 1 – Strongly disagree; 7 – Strongly agree.
+
 ## Step-Wise regression results {#sec-apx-stepwise}
@@
 ## Demographic Boxplots for World Values Survey {#sec-apx-box}
+
 ```{r}

### 2024-02-15 scripts/03-test_data.R
fixed tests

@@ -10,22 +10,21 @@
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
-# [...UPDATE THIS...]
 
 #### Read in data ####
 wvs_data_usa <- read_csv(here::here('outputs/data/wvs_data_usa.csv'))
 
 #### Test data ####
-test_that("Free Will scale scores are within the 1-6 range", {
-  expect_true(all(wvs_data_usa$freewill >= 1 & wvs_data_usa$freewill <= 6), 
-              info = "There are scores outside the 1-6 range in the Free Will 
+test_that("Free Will scale scores are within the 1-10 range", {
+  expect_true(all(wvs_data_usa$freewill >= 1 & wvs_data_usa$freewill <= 10 | is.na(wvs_data_usa$freewill)), 
+              info = "There are scores outside the 1-10 range in the Free Will 
               scale")
 })
 
 test_that("Job Satisfaction scale values are within the 1-7 range", {
   expect_true(all(wvs_data_usa$job_satisfaction >= 1 & 
-                    wvs_data_usa$job_satisfaction <= 7),
-              info = "Job Satisfaction scale values are out of the 1-7 range")
+                    wvs_data_usa$job_satisfaction <= 10 | is.na(wvs_data_usa$job_satisfaction)),
+              info = "Job Satisfaction scale values are out of the 1-10 range")
 })
 
 test_that("Data types are correct", {
@@ -45,7 +44,7 @@ test_that("Dataset has the expected number of rows", {
 test_that("Values in specified columns are positive", {
   columns_to_check <- c("freewill", "job_satisfaction")
   for (column_name in columns_to_check) {
-    expect_true(all(your_dataframe[[column_name]] > 0),
+    expect_true(all(wvs_data_usa[[column_name]] > 0 | is.na(wvs_data_usa[[column_name]])),
                 info = paste("Not all values in the", column_name, 
                              "column are positive."))
   }

### 2024-02-15 outputs/paper/paper.qmd
finished discussion section

@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## Effect of Free Will Beliefs
+The main result of our analysis is that the belief in free will is sufficient to positively influence one's job satisfaction.
+Both the Amazon Mechanical Turk and WVS data sources showed significant positive correlations between these two psychological constructs.
+Free will beliefs are found to be  integral to psychological well-being and motivation, and are commonly linked to agency, autonomy, and responsibility [@wang2009].
+By fostering an environment that supports these values, organizations can enhance job satisfaction and performance [@stillman2010].
+Moreover, we found that job autonomy is the most important factor in mediating the relationship between free will beliefs and job satisfaction.
+When employees feel they have the freedom to make decisions and control their work processes, this autonomy reinforces their free will beliefs, leading to higher job satisfaction [@goezukara2016].
+Our analysis shows that this applies directly to the workplace, since we found a robust effect of free will beliefs on job satisfaction, even when controlling for other psychological agency constructs, suggests a strong and direct relationship.
+As @clark2017 have found, belief in free will also alleviates distress and anxiety in regards to punishment and moral judgments, which can further positively impact satisfaction at work.
+This is crucial information, since it can help us effectively design targeted interventions with long-term benefits for employees and organizations [@feldman2017].
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Demographic Variable Effects
+Our findings suggest that while there are slight differences in the median belief in free will among different age groups, these differences do not reach statistical significance.
+This outcome indicates that the belief in free will might be relatively stable across different stages of adult life, not significantly impacted by age-related factors such as life experience and generational values, but rather by cultural factors @feltz2009.
+Our findings also suggest that a slight differences based on sex, with women reporting higher beliefs in free will.
+This finding could reflect underlying gender-related socialization processes, where differing societal expectations and roles for men and women might influence their perceptions of autonomy and control [@baumeister1988].
+However, even when found significant, this effect was marginal in both samples, suggesting that the influence of free will beliefs on job satisfaction might operate independently of these demographic factors.
+This independence has strong implications for potential interventions interventions aimed at enhancing employees' sense of autonomy and control could be broadly applicable and beneficial [@sheldon2001].
 
-## Second discussion point
+Nevertheless, unobserved demographic factors could have also contributed to the significant difference in free will beliefs and job satisfaction ratings between the Amazon MTurk sample and the WVS sample.
+Latter is much more representative due to its larger sample size, more thorough survey methodology, and more equal distribution of ages and occupations.
+The Amazon MTurk sample was much more restricted, with a much lower median age, and was not cross-occupational in the same sense the more comprehensive WVS sample is.
+The nature of Amazon MTurk as a novel and mostly low-wage job platform could also explain the comparatively lower job satisfaction rates and higher beliefs in free will.
 
-## Third discussion point
+## Cultural Differences
+Our findings indicate that correlations are now statistically significant for all countries in the sample which suggests a pervasive and possibly strengthening relationship between belief in free will and job satisfaction globally.
+This contrasts with Feldman et al.'s (2018) findings, where the significance of these correlations may have varied across countries.
+This change could be indicative of a global trend towards greater recognition of the importance of autonomy and personal agency in job satisfaction [@goezukara2016].
+Our finding that the United States has a high average belief in free will, second only to Mexico, can be contextualized within the framework of cultural values and individualism.
+Based on how American cultural norms and values are shaped by freedom, independence, and liberty, the perception and valuation of free will can be expected to be considerably higher than when compared to other countries, influencing the strength of its relationship with job satisfaction.
+Hofstede's cultural dimensions theory, which explores the impact of a society's culture on the values of its members and how these values relate to behavior, suggests that societies with high individualism scores tend to place a greater emphasis on personal freedom and autonomy, which could contribute to stronger beliefs in free will [@hofstede2001].
+Again, this has direct implications for interventions operating within the American context, suggesting a strong focus on such values and constructs to increase overall worker's satisfaction.
 
-## Weaknesses and next steps
+## Limitations
+Potential weaknesses include the overreliance on self-reporting measures, which are subject to biases; the cross-sectional nature of some studies, which limits causal inference; and the potential for cultural nuances to be oversimplified or to not be fully captured by the statistical measures used.
+Additionally, the concept of free will can vary significantly across different cultures.
+When dealing with constructs that deeply intertwine with personal identity and cultural beliefs it is very important to design survey questions appropriately and make sure to not overstep any boundaries.
+However, the resulting general nature of these questions could limit capturing the full scope of the concept.
+The standardized scales used to measure the constructs may have therefore not adequately captured the underlying construct, despite high reliability coefficients.
 
-Weaknesses and next steps should also be included.
+## Future Directions
+The next steps to take would be to further explore societal changes over time and individual differences in the value of free will, which would be possible due to the longitudinal nature of the WVS data.
+Further research couldalso  investigate the impact of emerging technologies and digital platforms on perceptions of free will, examining how online behavior and the emergence of artificial intelligence influences or reflects these beliefs.
+Additionally, interdisciplinary approaches combining psychology, sociology, and neuroscience could offer deeper insights into the biological underpinnings and social determinants of free will beliefs.
+Exploring these areas could significantly enhance our understanding of free will's role in modern society and individual psychology, and help us even more in designing appropriate interventions not only at the workspace but other spheres of our lives.
 
@@
 **Self-Control Scale**
+
 1. I am good at resisting temptation.
@@
 **Locus of Control**
+
 1.
@@
 **Self-esteem**
+
 1. I feel that I am a person of worth, at least on an equal basis with others.
@@
 **Self-efficacy**
+
 1. I am strong enough to overcome life's struggles.
@@
 **Implicit beliefs**
+
 1. The kind of person someone is, is something very basic about them, and it can't be changed

### 2024-02-15 outputs/paper/paper.qmd
polished paper

@@
 title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
-subtitle: "Nowhere near done yet! We had significant issues with our last dataset and had to restart, so bare with us."
 author: Sami El Sabri and Liban Timir
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study examines the relationship between belief in free will and job satisfaction in the United States, using data from Amazon Mechanical Turk and the World Values Survey.
+It replicates and extends previous findings by Feldman et al.
+(2017), confirming that free will belief positively correlates with job satisfaction in both samples.
+The analysis identifies job autonomy as a key mediator in this relationship.
+Results highlight the significant role of free will beliefs in enhancing workplace satisfaction and emphasize the importance of considering cultural and societal factors particular to the American context"
 format: pdf
+toc: true
 number-sections: true
@@
 The estimand is the correlation between the belief in free will and job satisfaction.
+Utilizing Amazon Mechanical Turk and World Values Survey data, we found that belief in free will significantly correlates with job satisfaction both at individual and national levels.
+Additionally, we found job autonomy as a critical mediator in this relationship, while other agency constructs and demographic factors play a less important role in impacting workplace satisfaction across diverse American contexts.
+We also found American participants to be among the world's highest believers in free will, further emphasizing the importance of considering the local context.
+
+We begin our paper with a closer look at the data source and measurement (@sec-data), followed by a selection of relevant results (@sec-results).
+Finally, we will conclude with a discussion of our findings to integrate our replication with the original paper by @feldman2017 and the broader literature on free will beliefs (@sec-discussion).
+We will also discuss potential ethical biases, limitations, and future directions.
 Our reproduction was conducted using the statistical programming language R [@citeR].
 In the data analysis and visualization process, we also made use of the following R packages: tidyverse [@citetidyverse], dplyr [@citedplyr], knitr [@citeknitr], kableExtra [@citekExtra], purrr [@citepurrr], psych [@citepsych], car [@citecar], MASS [@citeMASS], and countrycode [@citecc].
-
-We begin our paper with a closer look at the data source and measurement (@sec-data), followed by a selection of relevant results (@sec-results).
-Finally, we will conclude with a discussion of our findings to integrate our replication with the original paper by @feldman2017 and the broader literature on free will beliefs.
-We will also discuss potential ethical biases, limitations, and future directions.
-This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.
-\### TALK ABOUT FINDINGS HERE###
 
@@
            "Implicit Beliefs", "Self-Esteem", "Self-Efficacy", "Self-Control"),
-  "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2, alpha_locus, alpha_self_eff, alpha_self_est, alpha_implicit, alpha_self_con)
+  "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2, alpha_locus, alpha_self_eff, alpha_self_est, alpha_implicit, alpha_self_con), check.names = FALSE
 )
@@
 Using the aforementioned constructs which are derived from their respective set of survey questions, we were able to replicate all the means and standard deviations, as seen in @tbl-st2summary.
+@fig-fwbarst2 shows how in this sample, no participant indicated a free will belief rating less than 3, and that the distribution is strongly left-skewed.
+The distribution of ages, on the other hand, is right-skewed, with most participants being between 30 and 40 years old (@fig-agebarst2)
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-fwbarst2
+#| fig-cap: Distribution of Free Will Beliefs among Amazon MTurk workers as measured in Feldman et al. (2018)
+#| fig-width: 2.5
+#| fig-height: 2.5
+
+satisfaction_data_usa_rel %>% ggplot(aes(x=`Belief in Free Will (T1)`)) +
+  geom_histogram(binwidth = 0.5, fill = "lightblue", color = "black") +
+  xlim(0,6) +
+  labs(
+       x = "Belief in Free Will Rating",
+       y = "Frequency") +
+  theme_minimal()
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-agebarst2
+#| fig-cap: Distribution of Ages among Amazon MTurk workers as measured in Feldman et al. (2018)
+#| fig-width: 2.5
+#| fig-height: 2.5
+
+satisfaction_data_usa_rel %>% ggplot(aes(x=`Age`)) +
+  geom_histogram(binwidth = 4, fill = "lightblue", color = "black") +
+
+  labs(
+       x = "Age",
+       y = "Count") +
+  theme_minimal()
+```
 The World Values Survey dataset needed some additional cleaning steps, filtering for certain variables of interest and only for surveys based in the United States of America.
 See @tbl-wvssummary for summary statistics of selected psychological constructs.
+Similarly to the MTurk data, free will belief ratings are heavily left-skewed with most respondents indicating high beliefs in free will (@fig-fwbarwvs).
+The age distribution, however, is much more uniform than in the MTurk data, indicating greater representativeness of the sample (@fig-agebarwvs).
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-fwbarwvs
+#| fig-cap: "Distribution of Free Will Beliefs among WVS respondents 1981-2022"
+#| fig-width: 2.5
+#| fig-height: 2.5
+
+wvs_data_usa %>% ggplot(aes(x=freewill)) +
+  geom_bar(binwidth = 1, fill = "lightblue", color = "black") +
+  labs(
+       x = "Belief in Free Will Rating",
+       y = "Frequency") +
+  theme_minimal()
+```
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-agebarwvs
+#| fig-cap: Distribution of Ages among among WVS respondents 1981-2022
+#| fig-width: 2.5
+#| fig-height: 2.5
+
+wvs_data_usa %>% ggplot(aes(x=`Age`)) +
+  geom_histogram(binwidth = 4, fill = "lightblue", color = "black") +
+
+  labs(
+       x = "Age",
+       y = "Count") +
+  theme_minimal()
+```
+
+\newpage
 # Results {#sec-results}
@@
 Locus of control lacks any significant correlations, which together with its low reliability coefficient designates it as a less decisive control variable.
-The most important relationship, however, is between free will beliefs and job satisfaction: The belief in free will was significantly positively correlated with job satisfaction both at Time 1 (*r* = `r cor_fw_js1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`\]) and at Time 2 ( (r = `r cor_fw_js2_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js2_ci[1]`, `r cor_fw_js1_ci[2]`\])).
+The most important relationship, however, is between free will beliefs and job satisfaction: The belief in free will was significantly positively correlated with job satisfaction both at Time 1 (*r* = `r cor_fw_js1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js1_ci[1]`, `r cor_fw_js1_ci[2]`\]) and at Time 2 (r = `r cor_fw_js2_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_js2_ci[1]`, `r cor_fw_js1_ci[2]`\]).
 However, this correlation is not as strong as the one between free will beliefs and job autonomy (*r* = `r cor_fw_jaut1_correlation_coefficient`, *p* \<.001, CI \[`r cor_fw_jaut1_ci[1]`, `r cor_fw_jaut1_ci[2]`\]).
@@
 
-## Comparison to Amazon Mechanical Turk Sample
+### Comparison to Amazon Mechanical Turk Sample
 
@@
 
+fwconfint1 <- round(t_test_result_fw$conf.int[1],2)
+fwconfint2 <- round(t_test_result_fw$conf.int[2],2)
+
+jsconfint1 <- round(t_test_result_js$conf.int[1],2)
+jsconfint2 <- round(t_test_result_js$conf.int[2],2)
+
 ```
@@
 Since the two samples use different scales to measure belief in free will and job satisfaction, we normalized the values (mapping it onto a scale from 0 to 1), such that we can compare them directly (@tbl-comparison).
-Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* \< 0.001, CI \[`r t_test_result_fw$conf.int[1]`, `r t_test_result_fw$conf.int[2]`\]).
-The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* \< 0.001, CI \[`r t_test_result_js$conf.int[1]`, `r t_test_result_js$conf.int[2]`\]).
+Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* \< 0.001, CI \[`r fwconfint1 `, `r fwconfint2 `\]).
+The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* \< 0.001, CI \[`r jsconfint1`, `r jsconfint2`\]).
 

### 2024-02-15 outputs/ssrp_report/ssrp_report.qmd
made minor fixes to ssrp report

--- 2024-02-14 outputs/ssrp_report/ssrp_report.qmd
@@
   "Reliability Coefficient" = c(alpha_js1, alpha_js2, alpha_freewill, alpha_jaut1, alpha_jaut2,
-                                alpha_locus, alpha_implicit, alpha_selfest, alpha_selfeff, alpha_self_con),
+                                alpha_locus, alpha_implicit, alpha_self_est, alpha_self_eff, alpha_self_con),
   Mean = c(

### 2024-02-15 outputs/paper/paper.qmd
updated link to SSRP

@@
 ---
-title: "The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction"
+title: "You Best Believe: How Believing in Free Will is Enough to be More Satisfied at the Workplace"
 author: Sami El Sabri and Liban Timir
-thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis.
-SSRP replication available at: https://www.socialsciencereproduction.org/reproductions/94caaeaf-7e11-4efa-9269-7729fc2e0837/index"
+thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis. SSRP replication available at: https://doi.org/10.48152/ssrp-hrv5-ck80"
 date: 02-13-2024
@@
 The analysis identifies job autonomy as a key mediator in this relationship.
-Results highlight the significant role of free will beliefs in enhancing workplace satisfaction and emphasize the importance of considering cultural and societal factors particular to the American context"
+Results highlight the significant role of free will beliefs in enhancing workplace satisfaction and emphasize the importance of considering cultural and societal factors particular to the American context."
 format: pdf

### 2024-02-15 outputs/ssrp_report/ssrp_report.qmd
updated link to SSRP

@@
 author: Sami El Sabri and Liban Timir
-thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis"
+thanks: "Code and data are available at: https://github.com/samielsabri/freewill_analysis. SSRP replication available at: https://doi.org/10.48152/ssrp-hrv5-ck80"
 date: 02-13-2024

### 2024-02-15 outputs/paper/paper.qmd
changed title

@@
 ---
-title: "You Best Believe: How Believing in Free Will is Enough to be More Satisfied at the Workplace"
+title: "How Believing in Free Will is Enough to Be More Satisfied at Work"
 author: Sami El Sabri and Liban Timir

### 2024-02-17 outputs/paper/paper.qmd

@@
 This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al.
-paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey.
+paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national level, using the World Values Survey.
 We will also consider whether there are any significant differences between the national-level data and the Amazon Mechanical Turk data.
@@
 We will also discuss potential ethical biases, limitations, and future directions.
-Our reproduction was conducted using the statistical programming language R [@citeR].
-In the data analysis and visualization process, we also made use of the following R packages: tidyverse [@citetidyverse], dplyr [@citedplyr], knitr [@citeknitr], kableExtra [@citekExtra], purrr [@citepurrr], psych [@citepsych], car [@citecar], MASS [@citeMASS], and countrycode [@citecc].
+Our reproduction was conducted using the statistical programming language `R` [@citeR].
+In the data analysis and visualization process, we also made use of the following `R` packages: `tidyverse` [@citetidyverse], `dplyr` [@citedplyr], `knitr` [@citeknitr], `kableExtra` [@citekExtra], `purrr` [@citepurrr], `psych` [@citepsych], `car` [@citecar], `MASS` [@citeMASS], and `countrycode` [@citecc].
 
@@
   + How much pride, if any, do you take in the work that you do? (1 = "A great deal", 3 = "Little").
-  + We also inverted this scale, such that 1 means "Little" and 3 means "A great deal", making it making it more consistent with the ordering logic of other variables used.
+  + We also inverted this scale, such that 1 means "Little" and 3 means "A great deal", making it more consistent with the ordering logic of other variables used.
 
@@
 
-kable(reliability_scores)
+kable(reliability_scores,
+    booktabs = TRUE,
+    linesep = "")
 ```
@@
 
-kable(satisfaction_data_usa_summary)
+kable(satisfaction_data_usa_summary,
+    booktabs = TRUE,
+    linesep = ""
+)
 ```
@@
 
-kable(wvs_data_usa_summary)
+kable(wvs_data_usa_summary,
+booktabs = TRUE,
+    linesep = ""
+)
 
@@
 
-In exploring free will beliefs and their impact on job satisfaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends Feldman et al.'s results.
+In exploring free will beliefs and their impact on job satisfaction in the context of American Amazon Mechanical Turk workers, our study replicates and extends the results of @feldman2017.
 As seen in @fig-corst2, most variables are significantly correlated with each other, with the highest correlations being unsurprisingly between the two measurements of Job satisfaction.
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))  + theme_minimal()
-
 ```
@@
 Our analysis shows that this applies directly to the workplace, since we found a robust effect of free will beliefs on job satisfaction, even when controlling for other psychological agency constructs, suggests a strong and direct relationship.
-As @clark2017 have found, belief in free will also alleviates distress and anxiety in regards to punishment and moral judgments, which can further positively impact satisfaction at work.
+As @clark2017 have found, belief in free will also alleviates distress and anxiety in regard to punishment and moral judgments, which can further positively impact satisfaction at work.
 This is crucial information, since it can help us effectively design targeted interventions with long-term benefits for employees and organizations [@feldman2017].
@@
 This outcome indicates that the belief in free will might be relatively stable across different stages of adult life, not significantly impacted by age-related factors such as life experience and generational values, but rather by cultural factors @feltz2009.
-Our findings also suggest that a slight differences based on sex, with women reporting higher beliefs in free will.
+Our findings also suggest that a slight difference based on sex, with women reporting higher beliefs in free will.
 This finding could reflect underlying gender-related socialization processes, where differing societal expectations and roles for men and women might influence their perceptions of autonomy and control [@baumeister1988].
 However, even when found significant, this effect was marginal in both samples, suggesting that the influence of free will beliefs on job satisfaction might operate independently of these demographic factors.
-This independence has strong implications for potential interventions interventions aimed at enhancing employees' sense of autonomy and control could be broadly applicable and beneficial [@sheldon2001].
+This independence has strong implications for potential interventions aimed at enhancing employees' sense of autonomy and control could be broadly applicable and beneficial [@sheldon2001].
 
@@
 The next steps to take would be to further explore societal changes over time and individual differences in the value of free will, which would be possible due to the longitudinal nature of the WVS data.
-Further research couldalso  investigate the impact of emerging technologies and digital platforms on perceptions of free will, examining how online behavior and the emergence of artificial intelligence influences or reflects these beliefs.
+Further research could also  investigate the impact of emerging technologies and digital platforms on perceptions of free will, examining how online behavior and the emergence of artificial intelligence influences or reflects these beliefs.
 Additionally, interdisciplinary approaches combining psychology, sociology, and neuroscience could offer deeper insights into the biological underpinnings and social determinants of free will beliefs.
